---
title: "Environment curves vs performance"
author: "Laura Segura Hernández"
date: "10/17/2022"
output:
  html_document:
    df_print: paged
    theme: cerulean
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_knit$set(root.dir = "C:/Users/laus1/OneDrive - University of Nebraska-Lincoln/UNL/PhD Tesis/Methods/Thermolimit/Thermolimit data analyses")
getwd()
```

#Libraries
```{r}
library(lme4)
library(dplyr)
library(forcats)
library(NRES803)
library(olsrr)
library(broom)
library(ggplot2)
library(lmerTest)
```



# Performance data
## Calling the  data
```{r}
derivs2<-read.csv("Outputs/derivsdemography_manualtrim.csv")
derivs2<-derivs2%>%
  rename(ind=id.x)%>%
  filter(trial!=2) %>%
  filter(first2>=0)

data<-read.csv("Data/Environment/Datos pseudos summer 2022 - Data.csv")
data<-data%>%
  select(1,2,4) %>%
  rename(ind=ID)

derivs2<-left_join(derivs2, data, by="ind")

```





# Environmental data
The files used to get the environmental data were previously modified in the script named "Processing2 final data for models", located  in the folders Methods/HOBO dataloggers/Data CPBS summer 2020/Final data. 

## Looking at the overall microhabitat means (plant+topsoil)

```{r}
micro<-read.csv("./Data/Environment/microhabtempsmerge3means.csv")

colnames(micro)

micro<-micro%>%
  select(!contains("10cm"))%>%
  rename("date2"="date2.x.x",
         "time"="time.x.x",
         "SOILdead_site1"="SOILdead_tempDeadtopCPBS_G1.csvB.csv",
         "SOILdead_site2"="SOILdead_tempDeadtopCPBS_G2.csvB.csv",
         "SOILdead_site3"="SOILdead_tempDeadtopCPBS_G3.csvB.csv",
         "SOILdead_site4"="SOILdead_tempDeadtopCPBS_G4.csvB.csv",
         "SOILdead_site5"="SOILdead_tempDeadtopCPBS_G5.csvB.csv",
         "SOILdead_site6"="SOILdead_tempDeadtopCPBS_G6.csvB.csv",
         "SOILdead_site7"="SOILdead_tempDeadtopCPBS_G7.csvB.csv",
         "SOILdead_site8"="SOILdead_tempDeadtopCPBS_G8.csvB.csv",
         "SOILdead_site9"="SOILdead_tempDeadtopCPBS_G9.csvB.csv",
         "SOILlive_site1"="SOILlive_tempLivetopCPBS_G1.csvB.csv",
         "SOILlive_site2"="SOILlive_tempLivetopCPBS_2.csvB.csv",
         "SOILlive_site3"="SOILlive_tempLivetopCPBS_G3.csvB.csv",
         "SOILlive_site4"="SOILlive_tempCPBS_G4.csvB.csv",
         "SOILlive_site5"="SOILlive_tempCPBS_G5.csvB.csv",
         "SOILlive_site6"="SOILlive_tempLivetopCPBS_G6.csvB.csv",
         "SOILlive_site7"="SOILlive_tempLivetopCPBS_G7.csvB.csv",
         "SOILlive_site8"="SOILlive_tempLivetopCPBS_G8.csvB.csv",
         "SOILlive_site9"="SOILlive_tempLivetopCPBS_G9.csvB.csv",
         "PLANTdeadcore_site2"="PLANTdead_core2",
         "PLANTdeadleaves_site2"="PLANTdead_leaves2",
         "PLANTdeadcore_site3"="PLANTdead_core3",
         "PLANTdeadleaves_site3"="PLANTdead_leaves3",
         "PLANTdeadleaves_site6"="PLANTdead_leaves6",
         "PLANTdeadcore_site6"="PLANTdead_core6",
         "PLANTdeadcore_site8"="PLANTdead_core8",
         "PLANTdeadleaves_site8"="PLANTdead_leaves8",
         "PLANTliveleaves_site2"="PLANTlive_top_leaves2",
         "PLANTliveleaves_b_site2"="PLANTlive_bottom_leaves2",
         "PLANTliveleaves_site6"="PLANTlive_top_leaves6",
         "PLANTliveleaves_b_site6"="PLANTlive_bottom_leaves6",
         "PLANTliveleaves_site9"="PLANTlive_top_leaves9") %>%
  mutate(means2=apply(micro[,5:35],1, mean, na.rm=T), 
         diff=means-means2,
         tempcorr=means2,
         date2=as.POSIXct(date2, format="%m/%d/%y"))

colnames(micro)
```


### For the whole season
#### For the whole area
```{r}
meanline<-mean(micro$means2)
medianline<-median(micro$means2)
ggplot(micro, aes(x=means2))+
  geom_histogram()+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Microclimate temperature (Celsius)")+
  ylab("Frequency")+
  scale_x_continuous(limits=c(5,55))

ggsave(plot=last_plot(),filename="Climate_allseason_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

```


#### Plotting for all life stages
```{r}
##### Protonymphs
protos <- derivs2%>%
  filter(stage=="Protonymph")
  

meanline<-mean(micro$means2)
medianline<-median(micro$means2)


coeff<-10000
ggplot()+
  geom_histogram(micro, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(protos, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Proto_allseason_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  


##### Deutonymphs
deutos<- derivs2%>%
  filter(stage=="Deutonymph")
  

meanline<-mean(micro$means2)
medianline<-median(micro$means2)


coeff<-10000
ggplot()+
  geom_histogram(micro, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(deutos, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Deuto_allseason_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  

##### Tritonymphs
tritos<- derivs2%>%
  filter(stage=="Tritonymph")
  

meanline<-mean(micro$means2)
medianline<-median(micro$means2)


coeff<-10000
ggplot()+
  geom_histogram(micro, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(tritos, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Trito_allseason_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  

##### Males
males <- derivs2%>%
  filter(stage=="Male")
  

meanline<-mean(micro$means2)
medianline<-median(micro$means2)


coeff<-10000
ggplot()+
  geom_histogram(micro, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(males, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Male_allseason_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  


##### Females
females <- derivs2%>%
  filter(stage=="Female")
  

meanline<-mean(micro$means2)
medianline<-median(micro$means2)


coeff<-10000
ggplot()+
  geom_histogram(micro, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(females, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Female_allseason_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  
```


#### Separating by sites



### For the warmest month (July)
```{r}
july<-subset(micro, date2 >"2020-06-30" & date2 < "2020-08-01")
```
#### For the whole area
```{r}
meanline<-mean(july$means2)
medianline<-median(july$means2)
ggplot(july, aes(x=means2))+
  geom_histogram()+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Microlimate temperature (Celsius)")+
  ylab("Frequency")+
  scale_x_continuous(limits=c(5,55))
ggsave(plot=last_plot(),filename="Climate_July_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

```


#### Plotting for all life stages
```{r}
##### Protonymphs
protos <- derivs2%>%
  filter(stage=="Protonymph")
  

meanline<-mean(july$means2)
medianline<-median(july$means2)


coeff<-10000
ggplot()+
  geom_histogram(july, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(protos, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Proto_july_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  


##### Deutonymphs
deutos<- derivs2%>%
  filter(stage=="Deutonymph")
  

meanline<-mean(july$means2)
medianline<-median(july$means2)


coeff<-10000
ggplot()+
  geom_histogram(july, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(deutos, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Deuto_july_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  

##### Tritonymphs
tritos<- derivs2%>%
  filter(stage=="Tritonymph")
  

meanline<-mean(july$means2)
medianline<-median(july$means2)


coeff<-10000
ggplot()+
  geom_histogram(july, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(tritos, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Trito_july_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  

##### Males
males <- derivs2%>%
  filter(stage=="Male")
  

meanline<-mean(july$means2)
medianline<-median(july$means2)


coeff<-10000
ggplot()+
  geom_histogram(july, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(males, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Male_july_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  


##### Females
females <- derivs2%>%
  filter(stage=="Female")
  

meanline<-mean(july$means2)
medianline<-median(july$means2)


coeff<-10000
ggplot()+
  geom_histogram(july, mapping=aes(x=tempcorr))+
  geom_vline(xintercept=meanline, color="red")+
  geom_vline(xintercept=medianline, color="blue")+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Temperature (Celsius)")+
  scale_x_continuous(limits=c(5,55))+
  geom_line(females, mapping=aes(y=first2*coeff,x=tempcorr, color=as.factor(trial)), size=1.3)+
  scale_y_continuous("Frequency", sec.axis = sec_axis(~ ./coeff, name = "Rate optima (Oxygen (mg/L)/ time(min))")) + 
  facet_wrap(vars(ind))+
  labs(colour = "Trial")



ggsave(plot=last_plot(),filename="Female_july_allarea.jpg",  path="Outputs/Microclimate vs performance/",width=7, height=7, units="in")

  
```

## Looking at the deeper soil temperatures

```{r}
soil<-read.csv("../Data/Environment/soil10cmtempsmerge2.csv")
```


### For the whole season

### For the warmest month
