---
title: "Oxygen estimation"
author: "Laura Segura Hernández"
date: "2022-08-07"
output:
  html_document:
    df_print: paged
    theme: cerulean
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float: false
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_knit$set(root.dir = "C:/Users/laus1/OneDrive - University of Nebraska-Lincoln/UNL/PhD Tesis/Methods/Thermolimit/Thermolimit data analyses")
getwd()
```

This is the final code to use. The other script for oxygen estimation for some reason lost part of the code. I made this copy after that, with hopefully the whole code again. Use this file for the oxygen estimation, not the other (incomplete) one.

# Libraries
```{r}
library(data.table)
library(tidyr)
library(dplyr)
library(lubridate)
library(ggplot2)
library(readr)
library(stringr)
library(purrr)
library(knitr)
library(magick)
library(jpeg)
library(fuzzyjoin)
library(forcats)
library(ggpubr)
library(grid)


```

# Organizing data

## Getting objects from Temperature Analyses 
```{r}
load("Outputs/Temperature analyses.RData")
```
## Calling and arranging data

### Trial 2
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 2/" #MODIFY FOR EACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial2",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t2a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t2b<-t2a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=2,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~250, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~239,
                       str_detect(id, "ch2")~311,
                       str_detect(id, "ch3")~65,
                       str_detect(id, "ch4")~136,
                       str_detect(id, "ch5")~168,
                       str_detect(id, "ch6")~294,
                       str_detect(id, "ch7")~322,
                       str_detect(id, "ch8")~022,
                       str_detect(id, "ch9")~258,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Female",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Tritonymph",
                         str_detect(id, "ch2")~"Protonymph",
                       str_detect(id, "ch3")~"Female",
                       str_detect(id, "ch4")~"Deutonymph",
                       str_detect(id, "ch5")~"Male",
                       str_detect(id, "ch6")~"Protonymph",
                       str_detect(id, "ch7")~"Tritonymph",
                       str_detect(id, "ch8")~"Deutonymph",
                       #str_detect(id, "ch9")~"Male",
                       TRUE~"Male"),
         weight=case_when(str_detect(id, "ch10")~1.269, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~0.792,
                       str_detect(id, "ch2")~0.189,
                       str_detect(id, "ch3")~1.714,
                       str_detect(id, "ch4")~0.330,
                       str_detect(id, "ch5")~1.219,
                       str_detect(id, "ch6")~0.240,
                       str_detect(id, "ch7")~0.749,
                       str_detect(id, "ch8")~0.339,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~1.001),
         atm=round(33.864*28.81)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==2) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t2<- full_join(t2b, temp2, by="datetime2", suffix=c("",".temp")) 
  

head(t2) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox2<-t2 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox2) #MODIFY FOR EACH TRIAL

ggplot(ox2, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8.5,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 3
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 3/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial3",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t3a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t3b<-t3a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=3,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~010, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~231,
                       str_detect(id, "ch2")~029,
                       str_detect(id, "ch3")~087,
                       str_detect(id, "ch4")~166,
                       str_detect(id, "ch5")~300,
                       str_detect(id, "ch6")~121,
                       str_detect(id, "ch7")~014,
                       str_detect(id, "ch8")~271,
                       str_detect(id, "ch9")~143,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Female",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Tritonymph",
                         str_detect(id, "ch2")~"Male",
                       str_detect(id, "ch3")~"Protonymph",
                       str_detect(id, "ch4")~"Female",
                       str_detect(id, "ch5")~"Deutonymph",
                       str_detect(id, "ch6")~"Protonymph",
                       str_detect(id, "ch7")~"Deutonymph",
                       str_detect(id, "ch8")~"Tritonymph",
                       #str_detect(id, "ch9")~"Male",
                       TRUE~"Male"),
         weight=case_when(str_detect(id, "ch10")~1.228, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~0.931,
                       str_detect(id, "ch2")~0.924,
                       str_detect(id, "ch3")~0.251,
                       str_detect(id, "ch4")~1.376,
                       str_detect(id, "ch5")~0.289,
                       str_detect(id, "ch6")~0.189,
                       str_detect(id, "ch7")~0.347,
                       str_detect(id, "ch8")~0.647,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~1.021),
         atm=round(33.864*28.81)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==3) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t3<- full_join(t3b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t3) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox3<-t3 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox3) #MODIFY FOR EACH TRIAL

ggplot(ox3, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(7,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 4
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 4/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial4",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t4a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t4b<-t4a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=4,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~213, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~337,
                       str_detect(id, "ch2")~051,
                       str_detect(id, "ch3")~109,
                       str_detect(id, "ch4")~245,
                       str_detect(id, "ch5")~037,
                       str_detect(id, "ch6")~131,
                       str_detect(id, "ch7")~005,
                       str_detect(id, "ch8")~194,
                       str_detect(id, "ch9")~154,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Deutonymph",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Protonymph",
                         str_detect(id, "ch2")~"Deutonymph",
                       str_detect(id, "ch3")~"Tritonymph",
                       str_detect(id, "ch4")~"Male",
                       str_detect(id, "ch5")~"Female",
                       str_detect(id, "ch6")~"Tritonymph",
                       str_detect(id, "ch7")~"Female",
                       str_detect(id, "ch8")~"Male",
                       #str_detect(id, "ch9")~"Male",
                       TRUE~"Protonymph"),
         weight=case_when(str_detect(id, "ch10")~0.241, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~0.163,
                       str_detect(id, "ch2")~0.350,
                       str_detect(id, "ch3")~0.730,
                       str_detect(id, "ch4")~0.963,
                       str_detect(id, "ch5")~1.332,
                       str_detect(id, "ch6")~0.509,
                       str_detect(id, "ch7")~1.582,
                       str_detect(id, "ch8")~0.999,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~0.109),
         atm=round(33.864*28.90)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==4) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t4<- full_join(t4b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t4) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox4<-t4 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox4) #MODIFY FOR EACH TRIAL

ggplot(ox4, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 5
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 5/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial5",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t5a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t5b<-t5a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=5,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~324, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~024,
                       str_detect(id, "ch2")~253,
                       str_detect(id, "ch3")~025,
                       str_detect(id, "ch4")~003,
                       str_detect(id, "ch5")~290,
                       str_detect(id, "ch6")~244,
                       str_detect(id, "ch7")~257,
                       str_detect(id, "ch8")~032,
                       str_detect(id, "ch9")~159,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Protonymph",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Female",
                         str_detect(id, "ch2")~"Male",
                       str_detect(id, "ch3")~"Tritonymph",
                       str_detect(id, "ch4")~"Deutonymph",
                       str_detect(id, "ch5")~"Protonymph",
                       str_detect(id, "ch6")~"Female",
                       str_detect(id, "ch7")~"Male",
                       str_detect(id, "ch8")~"Tritonymph",
                       #str_detect(id, "ch9")~"Male",
                       TRUE~"Deutonymph"),
         weight=case_when(str_detect(id, "ch10")~0.158, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~1.472,
                       str_detect(id, "ch2")~0.900,
                       str_detect(id, "ch3")~0.688,
                       str_detect(id, "ch4")~0.328,
                       str_detect(id, "ch5")~0.166,
                       str_detect(id, "ch6")~1.454,
                       str_detect(id, "ch7")~0.946,
                       str_detect(id, "ch8")~0.613,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~0.278),
         atm=round(33.864*28.84)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==5) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t5<- full_join(t5b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t5) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox5<-t5 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox5) #MODIFY FOR EACH TRIAL

ggplot(ox5, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 6
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 6/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial6",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t6a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t6b<-t6a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=6,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~267, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~288,
                       str_detect(id, "ch2")~030,
                       str_detect(id, "ch3")~1000,
                       str_detect(id, "ch4")~287,
                       str_detect(id, "ch5")~218,
                       str_detect(id, "ch6")~238,
                       str_detect(id, "ch7")~165,
                       str_detect(id, "ch8")~298,
                       str_detect(id, "ch9")~066,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Deutonymph",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Deutonymph",
                         str_detect(id, "ch2")~"Female",
                       str_detect(id, "ch3")~"NA",
                       str_detect(id, "ch4")~"Tritonymph",
                       str_detect(id, "ch5")~"Tritonymph",
                       str_detect(id, "ch6")~"Male",
                       str_detect(id, "ch7")~"Protonymph",
                       str_detect(id, "ch8")~"Protonymph",
                       #str_detect(id, "ch9")~"Male",
                       TRUE~"Female"),
         weight=case_when(str_detect(id, "ch10")~0.221, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~0.257,
                       str_detect(id, "ch2")~1.583,
                       str_detect(id, "ch3")~1000,
                       str_detect(id, "ch4")~0.583,
                       str_detect(id, "ch5")~0.715,
                       str_detect(id, "ch6")~0.794,
                       str_detect(id, "ch7")~0.142,
                       str_detect(id, "ch8")~0.201,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~2.208),
         atm=round(33.864*28.81)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==6) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t6<- full_join(t6b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t6) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox6<-t6 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  filter(ind < 900) %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox6) #MODIFY FOR EACH TRIAL

ggplot(ox6, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 7
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 7/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial7",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t7a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t7b<-t7a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=7,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~274, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~235,
                       str_detect(id, "ch2")~216,
                       str_detect(id, "ch3")~1000,
                       str_detect(id, "ch4")~237,
                       str_detect(id, "ch5")~175,
                       str_detect(id, "ch6")~246,
                       str_detect(id, "ch7")~232,
                       str_detect(id, "ch8")~269,
                       str_detect(id, "ch9")~043,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Deutonymph",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Male",
                         str_detect(id, "ch2")~"Male",
                       str_detect(id, "ch3")~"NA",
                       str_detect(id, "ch4")~"Female",
                       str_detect(id, "ch5")~"Protonymph",
                       str_detect(id, "ch6")~"Female",
                       str_detect(id, "ch7")~"Tritonymph",
                       str_detect(id, "ch8")~"Tritonymph",
                       #str_detect(id, "ch9")~"Male",
                       TRUE~"Protonymph"),
         weight=case_when(str_detect(id, "ch10")~0.324, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~0.900,
                       str_detect(id, "ch2")~1.126,
                       str_detect(id, "ch3")~1000,
                       str_detect(id, "ch4")~1.345,
                       str_detect(id, "ch5")~0.213,
                       str_detect(id, "ch6")~1.937,
                       str_detect(id, "ch7")~0.748,
                       str_detect(id, "ch8")~0.622,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~0.139),
         atm=round(33.864*28.78)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==7) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t7<- full_join(t7b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t7) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox7<-t7 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  filter(ind < 900) %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox7) #MODIFY FOR EACH TRIAL

ggplot(ox7, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 8
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 8/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial8",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t8a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t8b<-t8a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=8,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~345, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~301,
                       str_detect(id, "ch2")~107,
                       str_detect(id, "ch3")~54,
                       str_detect(id, "ch4")~270,
                       str_detect(id, "ch5")~85,
                       str_detect(id, "ch6")~36,
                       str_detect(id, "ch7")~112,
                       str_detect(id, "ch8")~138,
                       str_detect(id, "ch9")~80,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Tritonymph",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Protonymph",
                         str_detect(id, "ch2")~"Male",
                       str_detect(id, "ch3")~"Tritonymph",
                       str_detect(id, "ch4")~"Deutonymph",
                       str_detect(id, "ch5")~"Female",
                       str_detect(id, "ch6")~"Protonymph",
                       str_detect(id, "ch7")~"Female",
                       str_detect(id, "ch8")~"Deutonymph",
                       #str_detect(id, "ch9")~"Male",
                       TRUE~"Male"),
         weight=case_when(str_detect(id, "ch10")~0.863, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~0.176,
                       str_detect(id, "ch2")~0.648,
                       str_detect(id, "ch3")~0.858,
                       str_detect(id, "ch4")~0.325,
                       str_detect(id, "ch5")~1.863,
                       str_detect(id, "ch6")~0.146,
                       str_detect(id, "ch7")~1.522,
                       str_detect(id, "ch8")~0.329,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~1.199),
         atm=round(33.864*28.72)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==8) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t8<- full_join(t8b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t8) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox8<-t8 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  filter(ind < 900) %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox8) #MODIFY FOR EACH TRIAL

ggplot(ox8, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 9
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 9/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial9",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t9a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t9b<-t9a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=9,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~007, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~242,
                       str_detect(id, "ch2")~035,
                       str_detect(id, "ch3")~146,
                       str_detect(id, "ch4")~153,
                       str_detect(id, "ch5")~334,
                       str_detect(id, "ch6")~264,
                       str_detect(id, "ch7")~1000,
                       str_detect(id, "ch8")~004,
                       str_detect(id, "ch9")~228,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Male",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Female",
                         str_detect(id, "ch2")~"Protonymph",
                       str_detect(id, "ch3")~"Male",
                       str_detect(id, "ch4")~"Tritonymph",
                       str_detect(id, "ch5")~"Deutonymph",
                       str_detect(id, "ch6")~"Deutonymph",
                       str_detect(id, "ch7")~"NA",
                       str_detect(id, "ch8")~"Female",
                       #str_detect(id, "ch9")~"Male",
                       TRUE~"Tritonymph"),
         weight=case_when(str_detect(id, "ch10")~0.983, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~1.775,
                       str_detect(id, "ch2")~0.185,
                       str_detect(id, "ch3")~1.118,
                       str_detect(id, "ch4")~0.551,
                       str_detect(id, "ch5")~0.302,
                       str_detect(id, "ch6")~0.342,
                       str_detect(id, "ch7")~1000,
                       str_detect(id, "ch8")~1.425,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~0.569),
         atm=round(33.864*28.66)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==9) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t9<- full_join(t9b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t9) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox9<-t9 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  filter(ind < 900) %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox9) #MODIFY FOR EACH TRIAL

ggplot(ox9, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 10
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 10/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial10",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t10a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t10b<-t10a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=10,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~179, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~048,
                       str_detect(id, "ch2")~158,
                       str_detect(id, "ch3")~079,
                       str_detect(id, "ch4")~145,
                       str_detect(id, "ch5")~057,
                       str_detect(id, "ch6")~251,
                       str_detect(id, "ch7")~248,
                       str_detect(id, "ch8")~314,
                       str_detect(id, "ch9")~212,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Tritonymph",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Deutonymph",
                         str_detect(id, "ch2")~"Female",
                       str_detect(id, "ch3")~"Female",
                       str_detect(id, "ch4")~"Male",
                       str_detect(id, "ch5")~"Tritonymph",
                       str_detect(id, "ch6")~"Male",
                       str_detect(id, "ch7")~"Male",
                       str_detect(id, "ch8")~"Deutonymph",
                       #str_detect(id, "ch9")~"",
                       TRUE~"Female"),
         weight=case_when(str_detect(id, "ch10")~0.653, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~0.451,
                       str_detect(id, "ch2")~1.178,
                       str_detect(id, "ch3")~1.781,
                       str_detect(id, "ch4")~0.929,
                       str_detect(id, "ch5")~0.866,
                       str_detect(id, "ch6")~0.941,
                       str_detect(id, "ch7")~0.864,
                       str_detect(id, "ch8")~0.188,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~1.582),
         atm=round(33.864*28.64)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==10) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t10<- full_join(t10b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t10) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox10<-t10 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  filter(ind < 900) %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox10) #MODIFY FOR EACH TRIAL

ggplot(ox10, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 11
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 11/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial11",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t11a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t11b<-t11a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=11,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~141, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~272,
                       str_detect(id, "ch2")~305,
                       str_detect(id, "ch3")~326,
                       str_detect(id, "ch4")~224,
                       str_detect(id, "ch5")~173,
                       str_detect(id, "ch6")~214,
                       str_detect(id, "ch7")~082,
                       str_detect(id, "ch8")~113,
                       str_detect(id, "ch9")~329,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Female",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Tritonymph",
                         str_detect(id, "ch2")~"Deutonymph",
                       str_detect(id, "ch3")~"Deutonymph",
                       str_detect(id, "ch4")~"Female",
                       str_detect(id, "ch5")~"Tritonymph",
                       str_detect(id, "ch6")~"Deutonymph",
                       str_detect(id, "ch7")~"Male",
                       str_detect(id, "ch8")~"Male",
                       #str_detect(id, "ch9")~"",
                       TRUE~"Tritonymph"),
         weight=case_when(str_detect(id, "ch10")~1.853, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~0.675,
                       str_detect(id, "ch2")~0.312,
                       str_detect(id, "ch3")~0.283,
                       str_detect(id, "ch4")~1.785,
                       str_detect(id, "ch5")~0.566,
                       str_detect(id, "ch6")~0.184,
                       str_detect(id, "ch7")~1.095,
                       str_detect(id, "ch8")~1.046,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~0.591),
         atm=round(33.864*28.55)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==11) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t11<- full_join(t11b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t11) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox11<-t11 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  filter(ind < 900) %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox11) #MODIFY FOR EACH TRIAL

ggplot(ox11, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 12
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 12/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial12",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t12a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t12b<-t12a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=12,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~339, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~256,
                       str_detect(id, "ch2")~341,
                       str_detect(id, "ch3")~18,
                       str_detect(id, "ch4")~83,
                       str_detect(id, "ch5")~50,
                       str_detect(id, "ch6")~201,
                       str_detect(id, "ch7")~211,
                       str_detect(id, "ch8")~317,
                       str_detect(id, "ch9")~335,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"Deutonymph",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Female",
                         str_detect(id, "ch2")~"Tritonymph",
                       str_detect(id, "ch3")~"Male",
                       str_detect(id, "ch4")~"Male",
                       str_detect(id, "ch5")~"Male",
                       str_detect(id, "ch6")~"Female",
                       str_detect(id, "ch7")~"Female",
                       str_detect(id, "ch8")~"Tritonymph",
                       #str_detect(id, "ch9")~"",
                       TRUE~"Deutonymph"),
         weight=case_when(str_detect(id, "ch10")~0.314, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~1.450,
                       str_detect(id, "ch2")~0.790,
                       str_detect(id, "ch3")~1.23,
                       str_detect(id, "ch4")~1.015,
                       str_detect(id, "ch5")~1.229,
                       str_detect(id, "ch6")~1.49,
                       str_detect(id, "ch7")~1.500,
                       str_detect(id, "ch8")~0.905,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~0.268),
         atm=round(33.864*28.58)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==12) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t12<- full_join(t12b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t12) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox12<-t12 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  filter(ind < 900) %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox12) #MODIFY FOR EACH TRIAL

ggplot(ox12, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

### Trial 13
```{r}
# creating vector for columns names
cnames<-c("date", "time", "logtime", "oxygen", "phase", "amplitude", "temperature")

# creating vector for path
path<-"Data/Oxygen/Trial 13/" #MODIFY FOR EEACH TRIAL

# Creating list of file names
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

# Renaming files to remove the "-"
newname <- sub('-','', list) ## new name
file.rename(file.path(path,list), file.path(path, newname)) ## renaming it.

# Creating list of file names again
list <- list.files(path = path, pattern=".*txt") # creates the list of all the txt files in the directory

#Reading all files at once
for (i in list) {
  filename <- paste0( "frame",sub(pattern = "(.*)\\..*$", replacement = "\\1", basename(i)))
  wd <- paste0(path, i)
  assign(filename, read.delim2(wd,sep=";", skip=38, header=F, col.names=cnames)) #CHECK FOR EACH TRIALS IF THE SAME NUMBRE OF ROWS APPLIES

}


# Merging all into a single table
pattern<-grep("framepstrial13",names(.GlobalEnv),value=TRUE) #MODIFY FOR EACH TRIAL
list2<-do.call("list",mget(pattern))

t13a<-bind_rows(list2, .id="id") #MODIFY FOR EACH TRIAL


# Adding and modifying data to phase files 
t13b<-t13a %>% #MODIFY FOR EACH TRIAL
  select(c("id", "date", "time", "logtime", "phase")) %>%
  mutate(trial=13,#MODIFY FOR EACH TRIAL
         date=mdy(date), #formatting date
         datetime=paste0(date," ", time), #copying date and time together
         datetime=as_datetime(datetime, format="%Y-%m-%d %I:%M:%S %p")-minutes(9), #adjusting pc time to real time
         datetime2=round_date(datetime, unit="minute"),
         channel=case_when(str_detect(id, "ch10")~10, # Assigning channels 
                       str_detect(id, "ch1")~1,
                       str_detect(id, "ch2")~2,
                       str_detect(id, "ch3")~3,
                       str_detect(id, "ch4")~4,
                       str_detect(id, "ch5")~5,
                       str_detect(id, "ch6")~6,
                       str_detect(id, "ch7")~7,
                       str_detect(id, "ch8")~8,
                       str_detect(id, "ch9")~9,
                       TRUE~0),
         ind=case_when(str_detect(id, "ch10")~1000, # Assigning individuals MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~296,
                       str_detect(id, "ch2")~263,
                       str_detect(id, "ch3")~156,
                       str_detect(id, "ch4")~073,
                       str_detect(id, "ch5")~171,
                       str_detect(id, "ch6")~002,
                       str_detect(id, "ch7")~247,
                       str_detect(id, "ch8")~233,
                       str_detect(id, "ch9")~028,
                       TRUE~0), 
         stage=case_when(str_detect(id, "ch10")~"NA",#Assigning stage MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~"Deutonymph",
                         str_detect(id, "ch2")~"Tritonymph",
                       str_detect(id, "ch3")~"Male",
                       str_detect(id, "ch4")~"Male",
                       str_detect(id, "ch5")~"Deutonymph",
                       str_detect(id, "ch6")~"Tritonymph",
                       str_detect(id, "ch7")~"Female",
                       str_detect(id, "ch8")~"Female",
                       #str_detect(id, "ch9")~"",
                       TRUE~"Tritonymph"),
         weight=case_when(str_detect(id, "ch10")~1000, # Assigning weights MODIFY FOR EACH TRIAL
                       str_detect(id, "ch1")~0.272,
                       str_detect(id, "ch2")~0.764,
                       str_detect(id, "ch3")~0.656,
                       str_detect(id, "ch4")~1.18,
                       str_detect(id, "ch5")~0.361,
                       str_detect(id, "ch6")~0.767,
                       str_detect(id, "ch7")~1.256,
                       str_detect(id, "ch8")~1.693,
                       #str_detect(id, "ch9")~1.001,
                       TRUE~0.866),
         atm=round(33.864*28.55)) #MODIFY FOR EACH TRIAL: 33.864 * pressure in inHg

# Getting temperature for this trial 
temp2<-all_corr %>%
  filter(trial==13) %>% #MODIFY FOR EACH TRIAL
  select(c("datetime2","datetime", "tempcorr", "ramp"))

#Merging phase and temperature data
t13<- full_join(t13b, temp2, by="datetime2", suffix=c("",".temp")) #MODIFY FOR EACH TRIAL 
  

head(t13) #MODIFY FOR EACH TRIAL

#Estimating Oxygen 
f<-pi/180
f


ox13<-t13 %>% #MODIFY FOR EACH TRIAL
  na.omit() %>%
  filter(ind < 900) %>%
  mutate(phase=as.numeric(phase),
         ind=as.factor(ind),
         logtime=as.numeric(logtime),
         phaseangle=62.14-0.08915*tempcorr,
         sternvolmer=0.04899+4.965*10^(-4)*tempcorr,
         bunsen=(48.998-1.335*tempcorr+2.755*10^(-2)*tempcorr^2-3.22*10^(-4)*tempcorr^3+1.598*10^(-6)*tempcorr^4)*10^(-3),
         tempK=tempcorr+273,
         watervapor=exp(52.57-(6690.9/tempK)-4.681*log(tempK)),
         oxysat=(tan((pi/180)*phaseangle)-tan((pi/180)*phase))/tan((pi/180)*phase)*sternvolmer,
         oxymgl=(atm-watervapor)/1013*oxysat*0.2095*bunsen*1000*(32/22.414)*10)

head(ox13) #MODIFY FOR EACH TRIAL

ggplot(ox13, aes(x=logtime, y=oxymgl,group=ind, color=stage))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")

```

Go back to each trial and annotate the best beginning and end of trial, and change it in the temperature data, then re-run this analysis again, to only get the curves that actual pertain to the trial (i.e. get it from the start and also remove the tail when it warms up again at the end)



# Merging trials into a single dataframe FALTA

```{r, eval=F}
oxall<-bind_rows(ox2,ox3,ox4,ox5,ox6,ox7,ox8,ox9,ox10,ox11,ox12,ox13) %>%
filter(!ind%in%c("25","65", "231","82","121", "235")) # Cambiar por individuos ahogados
  


write.csv(oxall,"Outputs/oxygenall_aftercodedeletion.csv")

```

# Trying which function to use
```{r}

# Filtering for a single individuals to just see the fit
func<-ox7%>%
  filter(ind==232) %>%
  group_by(logtime) %>%
  filter(duplicated(logtime|n()==2))

#Trying different curves
fit2<-lm(oxymgl~poly(logtime, 2, raw=TRUE), data=func)
fit3<-lm(oxymgl~poly(logtime, 3, raw=TRUE), data=func)
fit4<-lm(oxymgl~poly(logtime, 4, raw=TRUE), data=func)
fit5<-lm(oxymgl~poly(logtime, 5, raw=TRUE), data=func)
fit6<-lm(oxymgl~poly(logtime, 6, raw=TRUE), data=func)
fit7<-lm(oxymgl~poly(logtime, 7, raw=TRUE), data=func)
fit8<-lm(oxymgl~poly(logtime, 8, raw=TRUE), data=func)
fit9<-lm(oxymgl~poly(logtime, 9, raw=TRUE), data=func)
fit10<-lm(oxymgl~poly(logtime, 10, raw=TRUE), data=func)

# CReating a dataframe to build the prediction
logtime <- seq(1, 125, length=125)  

# Plotting each predicted function line to the real data
plot(func$logtime, func$oxymgl, pch=19, xlab='Logtime', ylab='Oxygen(mg/l)')
lines(logtime, predict(fit7, data.frame(x=logtime)), col='grey')
lines(logtime, predict(fit2, data.frame(x=logtime)), col='red')
lines(logtime, predict(fit3, data.frame(x=logtime)), col='purple')
lines(logtime, predict(fit4, data.frame(x=logtime)), col='blue')
lines(logtime, predict(fit5, data.frame(x=logtime)), col='orange')
lines(logtime, predict(fit6, data.frame(x=logtime)), col='green')
lines(logtime, predict(fit7, data.frame(x=logtime)), col='grey')
lines(logtime, predict(fit8, data.frame(x=logtime)), col='yellow')
lines(logtime, predict(fit9, data.frame(x=logtime)), col='red')
lines(logtime, predict(fit10, data.frame(x=logtime)), col='grey')

#calculated adjusted R-squared of each model

# The adjusted r squared is the percent of the variance of Y intact after subtracting the error of the model. The more the R Squared value the better the model is for that data frame.
summary(fit2)$adj.r.squared
summary(fit3)$adj.r.squared
summary(fit4)$adj.r.squared
summary(fit5)$adj.r.squared
summary(fit6)$adj.r.squared
summary(fit7)$adj.r.squared
summary(fit8)$adj.r.squared
summary(fit9)$adj.r.squared
summary(fit10)$adj.r.squared

coef7<-as.data.frame(fit7$coefficients)
a0<-coef7[1,1]
a1<-coef7[2,1]
a2<-coef7[3,1]
a3<-coef7[4,1]
a4<-coef7[5,1]
a5<-coef7[6,1]
a6<-coef7[7,1]
a7<-coef7[8,1] #cambiar a A
x<-func$logtime
form7<-expression((a7*x^7)+(a6*x^6)+(a5*x^5)+(a4*x^4)+(a3*x^3)+(a2*x^2)+(a1*x^1)+(a0*x^0))
d7<-D(form7, "x") 
d7b<-D(d7, "x")

ggplot(aes(x=logtime, y=oxymgl), data=func)+geom_point()
plot(x, func$oxymgl, pch=19, xlab='Logtime', ylab='Oxygen(mg/l)')
lines(logtime, predict(fit7, data.frame(x=logtime)), col='red')

#Primera derivada: tasa con la que consume oxigeno
d7b.data<-as.data.frame(eval(d7, envir=as.data.frame(x)))
colnames(d7b.data)<-"y1"
d7b.data$logtime<-func$logtime
ggplot(aes(x=logtime, y=y1), data=d7b.data)+geom_point()


#Segunda derivada: cruce con y=0 son los punto de cambio, puntos de inflexion donde la pendiente cambia hacia arriva o hacia abajo
d7b.data<-as.data.frame(eval(d7b, envir=as.data.frame(x)))
colnames(d7b.data)<-"y1"
d7b.data$logtime<-func$logtime
ggplot(aes(x=logtime, y=y1), data=d7b.data)+geom_point()+scale_x_continuous(breaks=c(0,10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120))

# Finding the values at which the second derivative=0
f=function(x) eval(d7b)
uniroot(f, c(0,125))

inflection<-polyroot(c((a2 *2), (a3 *3 * 2 ),(a4* 4 * 3 ), (a5 *5 * 4) , (a6 * 6 * 5 ), (a7 * 7 * 6 )))
inflec<-as.data.frame(inflection)


```

# Trying which function to use on a different individual
```{r}

# Filtering for a single individuals to just see the fit
func<-ox3%>%
  filter(ind=="87")# %>%
  #group_by(logtime) %>%
  #filter(duplicated(logtime|n()==2))

#Trying different curves
fit2<-lm(oxymgl~poly(logtime, 2, raw=TRUE), data=func)
fit3<-lm(oxymgl~poly(logtime, 3, raw=TRUE), data=func)
fit4<-lm(oxymgl~poly(logtime, 4, raw=TRUE), data=func)
fit5<-lm(oxymgl~poly(logtime, 5, raw=TRUE), data=func)
fit6<-lm(oxymgl~poly(logtime, 6, raw=TRUE), data=func)
fit7<-lm(oxymgl~poly(logtime, 7, raw=TRUE), data=func)
fit8<-lm(oxymgl~poly(logtime, 8, raw=TRUE), data=func)
fit9<-lm(oxymgl~poly(logtime, 9, raw=TRUE), data=func)
fit10<-lm(oxymgl~poly(logtime, 10, raw=TRUE), data=func)

# CReating a dataframe to build the prediction
logtime <- seq(1, 125, length=125)  

# Plotting each predicted function line to the real data
plot(func$logtime, func$oxymgl, pch=19, xlab='Logtime', ylab='Oxygen(mg/l)')
lines(logtime, predict(fit7, data.frame(x=logtime)), col='grey')
lines(logtime, predict(fit2, data.frame(x=logtime)), col='red')
lines(logtime, predict(fit3, data.frame(x=logtime)), col='purple')
lines(logtime, predict(fit4, data.frame(x=logtime)), col='blue')
lines(logtime, predict(fit5, data.frame(x=logtime)), col='orange')
lines(logtime, predict(fit6, data.frame(x=logtime)), col='green')
lines(logtime, predict(fit7, data.frame(x=logtime)), col='grey')
lines(logtime, predict(fit8, data.frame(x=logtime)), col='yellow')
lines(logtime, predict(fit9, data.frame(x=logtime)), col='red')
lines(logtime, predict(fit10, data.frame(x=logtime)), col='grey')

#calculated adjusted R-squared of each model

# The adjusted r squared is the percent of the variance of Y intact after subtracting the error of the model. The more the R Squared value the better the model is for that data frame.
summary(fit2)$adj.r.squared
summary(fit3)$adj.r.squared
summary(fit4)$adj.r.squared
summary(fit5)$adj.r.squared
summary(fit6)$adj.r.squared
summary(fit7)$adj.r.squared
summary(fit8)$adj.r.squared
summary(fit9)$adj.r.squared
summary(fit10)$adj.r.squared

coef7<-as.data.frame(fit7$coefficients)
a0<-coef7[1,1]
a1<-coef7[2,1]
a2<-coef7[3,1]
a3<-coef7[4,1]
a4<-coef7[5,1]
a5<-coef7[6,1]
a6<-coef7[7,1]
a7<-coef7[8,1] #cambiar a A
x<-func$logtime
form7<-expression((a7*x^7)+(a6*x^6)+(a5*x^5)+(a4*x^4)+(a3*x^3)+(a2*x^2)+(a1*x^1)+(a0*x^0))
d7<-D(form7, "x") 
d7b<-D(d7, "x")

ggplot(aes(x=logtime, y=oxymgl), data=func)+geom_point()
plot(x, func$oxymgl, pch=19, xlab='Logtime', ylab='Oxygen(mg/l)')
lines(logtime, predict(fit7, data.frame(x=logtime)), col='red')

#Primera derivada: tasa con la que consume oxigeno
d7b.data<-as.data.frame(eval(d7, envir=as.data.frame(x)))
colnames(d7b.data)<-"y1"
d7b.data$logtime<-func$logtime
ggplot(aes(x=logtime, y=y1), data=d7b.data)+geom_point()


#Segunda derivada: cruce con y=0 son los punto de cambio, puntos de inflexion donde la pendiente cambia hacia arriba o hacia abajo
d7b.data<-as.data.frame(eval(d7b, envir=as.data.frame(x)))
colnames(d7b.data)<-"y1"
d7b.data$logtime<-func$logtime
ggplot(aes(x=logtime, y=y1), data=d7b.data)+geom_point()+scale_x_continuous(breaks=c(0,10, 20, 30, 40, 50, 60, 70, 80, 90, 100, 110, 120))

# Finding the values at which the second derivative=0
#f=function(x) eval(d7b)
#uniroot(f, c(0,125))

inflection<-polyroot(c((a2 *2), (a3 *3 * 2 ),(a4* 4 * 3 ), (a5 *5 * 4) , (a6 * 6 * 5 ), (a7 * 7 * 6 )))
inflection
inflec<-as.data.frame(inflection)
#inflec$inflection<-as.numeric*inflec$inflection

```


# Calling the csv file to avoid running the whole code
```{r}
#Calling csv file to avoid running the whole code
#oxall<-read.csv("../Outputs/oxygenall.csv")
oxall<-read.csv("./Outputs/oxygenall_aftercodedeletion.csv") #Use this one
```

# Cutting out traces with weird patterns

## Individual 22
```{r}
ind22<-oxall %>%
filter(ind=="22")
ggplot(aes(x=logtime, y=oxymgl), data=ind22)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
ind22<-ind22 %>%
filter(!between(logtime, 75, 85))
ggplot(aes(x=logtime, y=oxymgl), data=ind22)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
```

## Individual 83
```{r}
ind83<-oxall %>%
filter(ind=="83")
ggplot(aes(x=logtime, y=oxymgl), data=ind83)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
ind83<-ind83 %>%
filter(!between(logtime, 70, 80))
ggplot(aes(x=logtime, y=oxymgl), data=ind83)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
```

## Individual 131
```{r}
ind131<-oxall %>%
filter(ind=="131")
ggplot(aes(x=logtime, y=oxymgl), data=ind131)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
ind131<-ind131 %>%
filter(!between(logtime, 72, 82))
ggplot(aes(x=logtime, y=oxymgl), data=ind131)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
```

## Individual 136
```{r}
ind136<-oxall %>%
filter(ind=="136")
ggplot(aes(x=logtime, y=oxymgl), data=ind136)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
ind136<-ind136 %>%
filter(!between(logtime, 72, 82))
ggplot(aes(x=logtime, y=oxymgl), data=ind136)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
```

## Individual 159
```{r}
ind159<-oxall %>%
filter(ind=="159")
ggplot(aes(x=logtime, y=oxymgl), data=ind159)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
ind159<-ind159 %>%
filter(!between(logtime, 65, 75))
ggplot(aes(x=logtime, y=oxymgl), data=ind159)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
```

## Individual 168
```{r}
ind168<-oxall %>%
filter(ind=="168")
ggplot(aes(x=logtime, y=oxymgl), data=ind168)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
ind168<-ind168 %>%
filter(!between(logtime, 75 ,90))
ggplot(aes(x=logtime, y=oxymgl), data=ind168)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
```

## Individual 267
```{r}
ind267<-oxall %>%
filter(ind=="267")
ggplot(aes(x=logtime, y=oxymgl), data=ind267)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
ind267<-ind267 %>%
filter(!between(logtime, 80, 90))
ggplot(aes(x=logtime, y=oxymgl), data=ind267)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
```

## Individual 270
```{r}
ind270<-oxall %>%
filter(ind=="270")
ggplot(aes(x=logtime, y=oxymgl), data=ind270)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
ind270<-ind270 %>%
filter(!between(logtime, 70, 80))
ggplot(aes(x=logtime, y=oxymgl), data=ind270)+geom_point() +theme_classic() + theme(text=element_text(size=15))+scale_x_continuous(breaks = seq(0, 120, by = 5))
```

## Creating new dataset with trimmed individuals
```{r}
oxall<-oxall%>%
filter(!ind%in%c("22","83", "131", "136", "159", "168", "267", "270")) %>%
bind_rows(ind22, ind83, ind131, ind136, ind159, ind168, ind267, ind270) %>% 
  filter_all(all_vars(!is.infinite(.)))
levels(as.factor(oxall$ind))
write.csv(oxall, "Outputs/oxall_trimmed.csv")
```





# Creating a loop to get data for all individuals 

Steps needed:
  1. Fit the polynomial function to each individual
  2. See the r.adjusted for each individual
  3. Extract the coefficient of the function for each individual
  4. Get the first and second derivatives
  5. Get the inflection points
  6. Clean the inflection points 
  7. Check the inflection points with the data
  8. Merge the inflection points with the data set (get at least ID, stage)
  9. Do statistical comparison
  

## 1. Adjusting a polynomial function to each individual

```{r}
# Creating separate lists, one for each individual
dat_list<-split(oxall, oxall$ind)


# Creating function for fitting model
# Creating function for fitting model
r2 = function(data) {
fit = lm(oxymgl~poly(logtime, 10, raw=TRUE), data = data)
output<-broom::glance(fit) #Getting adjusted r
suma<-broom::tidy(summary(fit)) #Getting parameters for model
merge(output, suma, all=TRUE)
}
a<-map_dfr(dat_list, r2, .id = "id") #Provides dataframe with adjusted R
write.csv(a,"./Outputs/modelfitting.csv")

```

## 2. Plotting the function to the data of each individual

```{r}
# Creating plots to see the fit
r3 = function(data) {
     fit = lm(oxymgl~poly(logtime, 10, raw=TRUE), data = data)
     id<-data[1,11]
     
     mypath <- file.path("Outputs/Function fit/",paste("Individual_", id, ".jpg", sep = ""))


      jpeg(file = mypath, width=20, height=12, units="cm", res=300)

        plot(data$logtime, data$oxymgl, pch=19, xlab='Logtime', ylab='Oxygen(mg/l)', main=paste("Function fit: Ind", id), cex.lab=1.5, cex.axis=1.25)
lines(data$logtime, predict(fit, data.frame(logtime=data$logtime)), col='red',lwd=2)
dev.off()
     }

map_dfr(dat_list, r3, .id = "id")
```


## 3. Getting the first and second derivative for each individual

```{r}
# Getting the derivatives for each individual
#a2<-split(a, a$id)
r4=function(data){
fit = lm(oxymgl~poly(logtime, 10, raw=TRUE), data = data)
coef7<-as.data.frame(fit$coefficients)
a0<-coef7[1,1]
a1<-coef7[2,1]
a2<-coef7[3,1]
a3<-coef7[4,1]
a4<-coef7[5,1]
a5<-coef7[6,1]
a6<-coef7[7,1]
a7<-coef7[8,1]
a8<-coef7[9,1]
a9<-coef7[10,1]
a10<-coef7[11,1]
#x<-ox3$logtime #Values from raw data
x <- seq(0, 125, by=0.20)
form7<-expression((a10*x^10)+(a9*x^9)+(a8*x^8)+(a7*x^7)+(a6*x^6)+(a5*x^5)+(a4*x^4)+(a3*x^3)+(a2*x^2)+(a1*x^1)+(a0*x^0))
d7<-D(form7, "x")
d7f.data<-as.data.frame(eval(d7, envir=as.data.frame(x)))
colnames(d7f.data)<-"y1"
d7f.data$logtime<-x
d7b<-D(d7, "x")
d7s.data<-as.data.frame(eval(d7b, envir=as.data.frame(x)))
colnames(d7s.data)<-"y1"
d7s.data$logtime<-x
deriv<-list("first"=d7f.data, "second"=d7s.data)
}
a3<-map_dfr(dat_list, r4, .id = "id") #Creates the list with the values of the derivatives

## Saving the second derivatives into a single dataframe
write.csv(a3, "./Outputs/derivatives.csv")

```

## 4.  Plotting the first derivative
```{r}
# Plotting the first derivative
r4first=function(data){
  fit = lm(oxymgl~poly(logtime, 10, raw=TRUE), data = data)
coef7<-as.data.frame(fit$coefficients)
a0<-coef7[1,1]
a1<-coef7[2,1]
a2<-coef7[3,1]
a3<-coef7[4,1]
a4<-coef7[5,1]
a5<-coef7[6,1]
a6<-coef7[7,1]
a7<-coef7[8,1]
a8<-coef7[9,1]
a9<-coef7[10,1]
a10<-coef7[11,1]
id<-data[1,11]
  #x<-ox3$logtime #Values from raw data
x <- seq(0, 125, by=0.20) 
 form7<-expression((a10*x^10)+(a9*x^9)+(a8*x^8)+(a7*x^7)+(a6*x^6)+(a5*x^5)+(a4*x^4)+(a3*x^3)+(a2*x^2)+(a1*x^1)+(a0*x^0))
d7<-D(form7, "x") 
d7f.data<-as.data.frame(eval(d7, envir=as.data.frame(x)))
colnames(d7f.data)<-"y1"
d7f.data$logtime<-x

mypath <- file.path("Outputs/First derivative plots/",paste("Individual_", id, ".jpg", sep = ""))


 jpeg(file = mypath, width=20, height=12, units="cm", res=300)



plot(d7f.data$logtime, d7f.data$y1*-1, pch=19, xlab='Logtime', ylab='Oxygen(mg/l)', main=paste("First derivative: Ind ", id), cex.lab=1.5, cex.axis=1.25, ylim=c(-0.04,0.04))
dev.off()
}

map(dat_list, r4first)
```

## 5. Plotting the second derivative

```{r}
# Plotting the second derivative
r4second=function(data){
   fit = lm(oxymgl~poly(logtime, 10, raw=TRUE), data = data)
coef7<-as.data.frame(fit$coefficients)
a0<-coef7[1,1]
a1<-coef7[2,1]
a2<-coef7[3,1]
a3<-coef7[4,1]
a4<-coef7[5,1]
a5<-coef7[6,1]
a6<-coef7[7,1]
a7<-coef7[8,1]
a8<-coef7[9,1]
a9<-coef7[10,1]
a10<-coef7[11,1]
id<-data[1,11]
  #x<-ox3$logtime #Values from raw data
  x <- seq(0, 125, by=0.20) 
   form7<-expression((a10*x^10)+(a9*x^9)+(a8*x^8)+(a7*x^7)+(a6*x^6)+(a5*x^5)+(a4*x^4)+(a3*x^3)+(a2*x^2)+(a1*x^1)+(a0*x^0))
d7<-D(form7, "x") 
d7b<-D(d7, "x")
d7s.data<-as.data.frame(eval(d7b, envir=as.data.frame(x)))
colnames(d7s.data)<-"y1"
d7s.data$logtime<-x

mypath <- file.path("Outputs/Second derivative plots/",paste("Individual_", id, ".jpg", sep = ""))


 jpeg(file = mypath, width=20, height=12, units="cm", res=300)
plot(d7s.data$logtime, d7s.data$y1, pch=19, xlab='Logtime', ylab='Oxygen(mg/l)', main=paste("Second derivative: Ind", id), cex.lab=1.5, cex.axis=1.25, ylim=c(-0.004,0.004))
abline(h=0,col="orange", lty=2, lwd=2)
dev.off()
}

map(dat_list, r4second)
```

## 6. Getting the inflection points

```{r}
# Getting the inflection points: the points where there was a change in the "slope"
r5=function(data){
  fit = lm(oxymgl~poly(logtime, 10, raw=TRUE), data = data)
coef7<-as.data.frame(fit$coefficients)
a0<-coef7[1,1]
a1<-coef7[2,1]
a2<-coef7[3,1]
a3<-coef7[4,1]
a4<-coef7[5,1]
a5<-coef7[6,1]
a6<-coef7[7,1]
a7<-coef7[8,1]
a8<-coef7[9,1]
a9<-coef7[10,1]
a10<-coef7[11,1]
id<-data[1,11]
#x<-ox3$logtime #Values from raw data
x <- seq(0, 125, by=0.20)
form7<-expression((a10*x^10)+(a9*x^9)+(a8*x^8)+(a7*x^7)+(a6*x^6)+(a5*x^5)+(a4*x^4)+(a3*x^3)+(a2*x^2)+(a1*x^1)+(a0*x^0))
d7<-D(form7, "x")
d7b<-D(d7, "x")
inflection<-polyroot(c((a2 *2), (a3 *3 * 2 ),(a4* 4 * 3 ), (a5 *5 * 4) , (a6 * 6 * 5 ), (a7 * 7 * 6 ),(a8 *8*7), (a9*9*8), (a10*10*9)))
inflec<-as.data.frame(inflection)
inflec$id<-data[1,1]
as.data.frame(inflec)
}
a4<-map_dfr(dat_list, r5, .id = "id") # List of dataframes containing the inflection points


## Merging points into a single dataframe
options(scipen=999) #Removing scientific notation
inflections<-a4%>%
bind_rows() %>%
mutate(real=Re(inflection), #Extracting the real number from the complex expression
values=format(real, scientific=FALSE, big.mark=","), #Coverting the real number to printed decimal expression
rounded=round(real, digits=2), #rounding the real number
imagine=round(Im(inflection), digits=2)) %>% #Extracting te imaginary number
filter(between(real, 10, 115))
write.csv(inflections, "./Outputs/inflections.csv")
  

```


## 7.  Making combined figures for the function fit, first and second derivatives

```{r}
# AS a function
make_grid <- function(id){
  #Establishing paths
  f1<-paste0("Outputs/Function fit/Individual_",id,".jpg")
  f2<-paste0("Outputs/First derivative plots/","Individual_",id,".jpg")
  f3<-paste0("Outputs/Second derivative plots/","Individual_",id,".jpg")
  #Reading images
 j1<-readJPEG(f1)
 j2<-readJPEG(f2)
 j3<-readJPEG(f3)
  #Establishing path
 mypath <- file.path("C:/Users/laus1/OneDrive - University of Nebraska-Lincoln/UNL/PhD Tesis/Methods/Thermolimit/Thermolimit data analyses/Outputs/Figure montages/", paste("Individual_", id, ".jpg", sep = ""))
# Creating figures
jpeg(file = mypath, width=20, height=36, units="cm", res=300)
par(mar=c(1,1,1,1))
layout(matrix(1:3, ncol=1,byrow=TRUE))
 plot(NA,xlim=0:1,ylim=0:1,xaxt="n",yaxt="n")
 rasterImage(j1,0,0,1,1)
 plot(NA,xlim=0:1,ylim=0:1,xaxt="n",yaxt="n")
 rasterImage(j2, 0,0,1,1)
 plot(NA,xlim=0:1,ylim=0:1,xaxt="n",yaxt="n")
rasterImage(j3, 0,0,1,1)
dev.off()
 
  }

groups<-levels(as.factor(a$id))

map(groups, make_grid)


```

## 8. Obtaining the maximum rate of oxygen consumption (Ropt)
```{r}
derivs<-read.csv("Outputs/derivatives.csv")


derivs<-derivs %>%
  mutate(first2=first.y1*-1)%>% #Converting the slopes to positive
  filter(between(first.logtime, 30, 105)) #Triming the timeframe to the actual slope time
  
# Plotting to see if the conversion looks right
derivs%>%
  filter(id==10) %>%
  ggplot(aes(x=first.logtime, y=first2))+geom_line()

derivs%>%
  filter(id==3) %>%
  ggplot(aes(x=first.logtime, y=first2))+geom_line()

# Getting the row with the maximum value for each individual
ropt<-derivs %>%
     group_by(id) %>%
     slice(which.max(first2))%>%
  mutate(logtime=first.logtime,
         ind=id)


```

## 9. Getting the temperatures associated with the Ropt (Topt)
```{r}
#Merging the temperatures
topt<-difference_left_join(ropt,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup()


#getting the other demographic data
toptfinal<-oxall %>%
  select(c("date", "trial", "channel", "ind", "stage", "weight", "ramp")) %>%
  group_by(ind)%>%
  filter(row_number()==1) %>%
  right_join(topt, by=c("ind"="ind.x")) %>%
  rename(logtime=logtime.x,
         tempcorr=tempcorr2,
         ropt1=first.y1, 
         ropt2=first2) %>%
  ungroup()%>%
  mutate(stage=fct_relevel(stage, levels=c("Protonymph", "Deutonymph", "Tritonymph", "Female", "Male" )))

levels(toptfinal$stage)
#Visualizing the topt and Ropt

## Temperature optima
ggplot(toptfinal, aes(x=stage, y=tempcorr))+geom_boxplot() +theme_classic() + 
  theme(text = element_text(size = 15))+
  xlab("Stage")+
  ylab("Ctmax (Celsius)")

ggplot(toptfinal, aes(x=stage, y=ropt2))+geom_boxplot() +theme_classic() + 
  theme(text = element_text(size = 15))+
  xlab("Stage")+
  ylab("Maximum rate of oxygen consumption")


write.csv(toptfinal, "Outputs/ToptandRopts.csv")
```
### Checking the oxygen traces per life stage

### Protonymphs
```{r}
protos <- oxall%>%
  filter(stage=="Protonymph")
  
  
ggplot(protos, aes(x=logtime, y=oxymgl,group=ind, color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")+
  ggtitle("Protonymphs")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="OxygenTrace_Protonymphs.jpg",  path="../Outputs/Oxygen traces/")

  
```
### Deutonymphs
```{r}
deutos <- oxall%>%
  filter(stage=="Deutonymph")
  
  
ggplot(deutos, aes(x=logtime, y=oxymgl,group=ind, color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")+
  ggtitle("Protonymphs")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="OxygenTrace_Deutonymphs.jpg",  path="../Outputs/Oxygen traces/")

  
```
### Tritonymphs
```{r}
Tritos <- oxall%>%
  filter(stage=="Tritonymph")
  
  
ggplot(Tritos, aes(x=logtime, y=oxymgl,group=ind, color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")+
  ggtitle("Tritonymphs")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="OxygenTrace_Tritonymphs.jpg",  path="../Outputs/Oxygen traces/")

  
```
### Males
```{r}
males <- oxall%>%
  filter(stage=="Male")
  
  
ggplot(males, aes(x=logtime, y=oxymgl,group=ind, color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")+
  ggtitle("Males")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="OxygenTrace_Males.jpg",  path="../Outputs/Oxygen traces/")

  
```

### Females
```{r}
females <- oxall%>%
  filter(stage=="Female")
  
  
ggplot(females, aes(x=logtime, y=oxymgl,group=ind, color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  ylim(8,12) +
  facet_wrap(~ind)+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L")+
  ggtitle("Females")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="OxygenTrace_Females.jpg",  path="../Outputs/Oxygen traces/")

  
```
### Checking the slope trends per life stage


```{r}

derivs<-derivs %>%
  mutate(first2=first.y1*-1)%>% #Converting the slopes to positive
  filter(between(first.logtime, 30, 105)) #Triming the timeframe to the actual slope time


oxall<-read.csv("Outputs/oxall_trimmed.csv")

#Protonymphs
oxallp<-oxall %>%
  select(c("date", "trial", "channel", "ind", "stage", "weight", "ramp", "logtime")) %>%
  mutate(id=ind,
         first.logtime=logtime)%>% 
  filter(between(logtime, 30, 105)) %>%
  filter(stage=="Protonymph")

#Merging the temperatures
derivsp<-difference_right_join(derivs,oxallp, by=c("id","first.logtime"), max_dist=0.13) #Merges dataframes based on the closest logtime value (within 0.13)
  

#Deutonymphs  
oxalld<-oxall %>%
  select(c("date", "trial", "channel", "ind", "stage", "weight", "ramp", "logtime")) %>%
  mutate(id=ind,
         first.logtime=logtime)%>% 
  filter(between(logtime, 30, 105)) %>%
  filter(stage=="Deutonymph")

#Merging the temperatures
derivsd<-difference_right_join(derivs,oxalld, by=c("id","first.logtime"), max_dist=0.13) #Merges dataframes based on the closest logtime value (within 0.13)
  

#Tritonymphs  
oxallt<-oxall %>%
  select(c("date", "trial", "channel", "ind", "stage", "weight", "ramp", "logtime")) %>%
  mutate(id=ind,
         first.logtime=logtime)%>% 
  filter(between(logtime, 30, 105)) %>%
  filter(stage=="Tritonymph")

#Merging the temperatures
derivst<-difference_right_join(derivs,oxallt, by=c("id","first.logtime"), max_dist=0.13) #Merges dataframes based on the closest logtime value (within 0.13)


#Males 
oxallm<-oxall %>%
  select(c("date", "trial", "channel", "ind", "stage", "weight", "ramp", "logtime")) %>%
  mutate(id=ind,
         first.logtime=logtime)%>% 
  filter(between(logtime, 30, 105)) %>%
  filter(stage=="Male")

#Merging the temperatures
derivsm<-difference_right_join(derivs,oxallm, by=c("id","first.logtime"), max_dist=0.13) #Merges dataframes based on the closest logtime value (within 0.13)

#Females 
oxallf<-oxall %>%
  select(c("date", "trial", "channel", "ind", "stage", "weight", "ramp", "logtime")) %>%
  mutate(id=ind,
         first.logtime=logtime)%>% 
  filter(between(logtime, 30, 105)) %>%
  filter(stage=="Female")

#Merging the temperatures
derivsf<-difference_right_join(derivs,oxallf, by=c("id","first.logtime"), max_dist=0.13) #Merges dataframes based on the closest logtime value (within 0.13)


  
derivsdemography<- bind_rows(derivsp, derivsd, derivst, derivsm, derivsf)  
write.csv(derivsdemography, "Outputs/derivsdemography.csv")

derivs2<-read.csv("Outputs/derivsdemography.csv")
```


### Protonymphs
```{r}
protos <- derivs2%>%
  filter(stage=="Protonymph")
  
  
ggplot(protos, aes(x=logtime, y=first2,color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  facet_wrap(~ind)+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L)/time (min)")+
  ggtitle("Protonymphs")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="DerivsTrace_Protonymphs.jpg",  path="Outputs/Derivative traces per stage/")

  
```
### Deutonymphs
```{r}
deutos <- derivs2%>%
  filter(stage=="Deutonymph")
  
  
ggplot(deutos, aes(x=logtime, y=first2,color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  facet_wrap(~ind)+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L)/time (min)")+
  ggtitle("Deutonymphs")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="DerivsnTrace_Deutonymphs.jpg",  path="Outputs/Derivative traces per stage/")

  
```
### Tritonymphs
```{r}
Tritos <- derivs2%>%
  filter(stage=="Tritonymph")
  
  
ggplot(Tritos, aes(x=logtime, y=first2,color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  facet_wrap(~ind)+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L)/time (min)")+
  ggtitle("Tritonymphs")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="DerivsTrace_Tritonymphs.jpg",  path="Outputs/Derivative traces per stage/", width=7, height=7, units="in")

  
```

### Males
```{r}
males <- derivs2%>%
  filter(stage=="Male")
  
  
ggplot(males, aes(x=logtime, y=first2,color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  facet_wrap(~ind)+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L)/time (min)")+
  ggtitle("Males")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="DerivsTrace_Males.jpg",  path="Outputs/Derivative traces per stage/")

  
```

### Females
```{r}
females <- derivs2%>%
  filter(stage=="Female")
  
  
ggplot(females, aes(x=logtime, y=first2,color=as.factor(trial)))+ #MODIFY FOR EACH TRIAL
  geom_line()+
  facet_wrap(~ind)+
  theme_classic()+
  theme(text = element_text(size = 15), plot.title = element_text(size = (12)))+
  xlab("Time logged (min)")+
  ylab("Oxygen (mg/L)/time (min)")+
  ggtitle("Females")+
  labs(colour = "Trial")

ggsave(plot=last_plot(),filename="DerivsTrace_Females.jpg",  path="Outputs/Derivative traces per stage/")

  
```

## 10. Getting the activation energy

For this I need to do the following to each individual:
1. Trim the first derivative from the closests left-sided minimum to the maximum value
2. Join the logtime from the trimmed derivative in 1, to the portion of temps associated on oxall
3. convert the temps to Kelvin
4. Log transform (ln) the derivate and the temps in Kelvin
5. Get the slope of 4
6. Save such slope in a dataframe
7. Put everything in a single dataframe

8. Associate demographic data to each id

### Trimming the first derivative for each individual

```{r}
# Creating dataframe of manually cropped trends first
## Run Code chunk 36 first

## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
derivstrim<-derivs%>%
  filter(id=="2") %>% #filtering to each individual
  filter(between(first.logtime, 35, 65)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)

indiv<-derivs%>%
  filter(id=="3") %>% #filtering to each individual
  filter(between(first.logtime, 35, 65)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="4") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="5") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="7") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="10") %>% #filtering to each individual
  filter(between(first.logtime, 35, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="14") %>% #filtering to each individual
  filter(between(first.logtime, 35, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="18") %>% #filtering to each individual
  filter(between(first.logtime, 35, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="22") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="24") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="28") %>% #filtering to each individual
  filter(between(first.logtime, 40, 90)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="29") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="30") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="32") %>% #filtering to each individual
  filter(between(first.logtime, 20, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="35") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="36") %>% #filtering to each individual
  filter(between(first.logtime, 30, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="37") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

#Changed
indiv<-derivs%>%
  filter(id=="43") %>% #filtering to each individual
  filter(between(first.logtime, 30, 55)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="48") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="50") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="54") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="57") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="66") %>% #filtering to each individual
  filter(between(first.logtime, 50, 90)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="73") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="79") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="80") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="83") %>% #filtering to each individual
  filter(between(first.logtime, 30, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="85") %>% #filtering to each individual
  filter(between(first.logtime, 30, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="87") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="107") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="109") %>% #filtering to each individual
  filter(between(first.logtime, 30, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="112") %>% #filtering to each individual
  filter(between(first.logtime, 30, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="113") %>% #filtering to each individual
  filter(between(first.logtime, 45, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="131") %>% #filtering to each individual
  filter(between(first.logtime, 30, 65)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="136") %>% #filtering to each individual
  filter(between(first.logtime, 45, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="138") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="143") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="145") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="146") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="153") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

#Changed
indiv<-derivs%>%
  filter(id=="154") %>% #filtering to each individual
  filter(between(first.logtime, 30,60)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="156") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="158") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="159") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="165") %>% #filtering to each individual
  filter(between(first.logtime, 40, 90)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="166") %>% #filtering to each individual
  filter(between(first.logtime, 35, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="168") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="171") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="175") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="179") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="194") %>% #filtering to each individual
  filter(between(first.logtime, 50, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="201") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="211") %>% #filtering to each individual
  filter(between(first.logtime, 35, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="212") %>% #filtering to each individual
  filter(between(first.logtime, 30, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="214") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="216") %>% #filtering to each individual
  filter(between(first.logtime, 30, 60)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="218") %>% #filtering to each individual
  filter(between(first.logtime, 20, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="224") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="228") %>% #filtering to each individual
  filter(between(first.logtime, 60, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="232") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="233") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="237") %>% #filtering to each individual
  filter(between(first.logtime, 30, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="238") %>% #filtering to each individual
  filter(between(first.logtime, 20, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="239") %>% #filtering to each individual
  filter(between(first.logtime, 40, 60)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="242") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="244") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="245") %>% #filtering to each individual
  filter(between(first.logtime, 20, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="246") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="247") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="248") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="250") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="251") %>% #filtering to each individual
  filter(between(first.logtime, 40, 60)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="253") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="256") %>% #filtering to each individual
  filter(between(first.logtime, 30, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="257") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="258") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="263") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="264") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="267") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="269") %>% #filtering to each individual
  filter(between(first.logtime, 50, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="270") %>% #filtering to each individual
  filter(between(first.logtime, 60, 100)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="271") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="272") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="274") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="287") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="288") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="290") %>% #filtering to each individual
  filter(between(first.logtime, 35, 65)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="294") %>% #filtering to each individual
  filter(between(first.logtime, 50, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="296") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="298") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="300") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)


indiv<-derivs%>%
  filter(id=="305") %>% #filtering to each individual
  filter(between(first.logtime, 60, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

#***
indiv<-derivs%>%
  filter(id=="311") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="314") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="317") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="322") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="324") %>% #filtering to each individual
  filter(between(first.logtime, 30, 65)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="326") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="329") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="334") %>% #filtering to each individual
  filter(between(first.logtime, 60, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="335") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="337") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="339") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="341") %>% #filtering to each individual
  filter(between(first.logtime, 30, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="345") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

###

indiv<-derivs%>%
  filter(id=="51") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="141") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="173") %>% #filtering to each individual
  filter(between(first.logtime, 20, 60)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)

indiv<-derivs%>%
  filter(id=="213") %>% #filtering to each individual
  filter(between(first.logtime, 30, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)  

indiv<-derivs%>%
  filter(id=="301") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
derivstrim<- bind_rows(derivstrim, indiv)


write.csv(derivstrim, "Outputs/derivsmanualtrim.csv")
```

Check first deriv plot for 87
Check first deriv ind 141,173, 213,301

51 deuto
141  female
213 deuto
301 proto
87 proto
173 trito
213 deuto


### Creating the functions to get the activation energy for each individual


```{r}
# Creating separate lists, one for each individual
oxall<-read.csv("Outputs/oxall_trimmed.csv")

dat_list<-split(derivstrim, derivstrim$id)

#Creating plots for al individuals
energy<-data.frame(matrix(ncol = 4, nrow = 0))
colnames(energy)<-c("ind", "slope", "min", "max")

e2 = function(data) {
     min<-data %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
     max<-data %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
data2<-data %>% filter(between(first.logtime, min[1,1], max[1,1]))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
#plotting trim deriv
ind<-data[2,2]
label<-paste("Individual ", ind, sep = "")
data2 %>%  ggplot(aes(x=logtime, y=first2))+geom_line() + theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+ xlab("Time (min)")+  ylab("Slope (first derivative)")  #Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/First deriv trim/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

## 2, 3, 4: Join data, kelvin and log transformations
data3<-difference_left_join(data2,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=data3)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
data3 %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)
     }

map(dat_list, e2)


# Creating dataframe with the activation energy
e3 = function(data) {
     min<-data %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
     max<-data %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
data2<-data %>% filter(between(first.logtime, min[1,1], max[1,1]))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
data2 %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
data3<-difference_left_join(data2,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=data3)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-data[2,2]
dataframe<-data.frame(ind, slope, min[1,1], max[1,1])
#energy2<- bind_rows(energy2, dataframe)
     }

energy<-map_dfr(dat_list, e3, .id = "id")
colnames(energy)<-c("id", "ind", "slope", "min", "max")



write.csv(energy,"../Outputs/activation energy.csv")




```

## Adding the demographic data
```{r}
# At the end: adding demographic data (pending modification)
#getting the other demographic data

energyfinal<-oxall %>%
  select(c("date", "trial", "channel", "ind", "stage", "weight", "ramp")) %>%
  group_by(ind)%>%
  filter(row_number()==1) %>%
  right_join(energy, by=c("ind"="ind")) %>%
   ungroup()%>%
  mutate(stage=fct_relevel(stage, levels=c("Protonymph", "Deutonymph", "Tritonymph", "Female", "Male" ))) %>%
  arrange(stage)
levels(energyfinal$stage)

write.csv(energyfinal, "./Outputs/activation energy final.csv")
#date, time, datetime, channel, stage, weight, ramp
  
```

# Assessing the activation energy data
```{r}
## Temperature optima
ggplot(energyfinal, aes(x=stage, y=slope))+geom_boxplot() +theme_classic() + 
  theme(text = element_text(size = 15))+
  xlab("Stage")+
  ylab("Activation energy") # Check what units this would be


```

# Estimating Topt and Ropt from the manual trim trend for those nymphs with very high topts

```{r}
# Calling the file that was created in code chunk 49 (manually trimming before the activation curves)

derivstrim<-read.csv("Outputs/derivsmanualtrim.csv")

#Individuals to redo
ids<-c(165,301,36,337,324,154,43,288,274,171,314,300,213,22,270,345,239,168)


derivst<-derivstrim %>%
  filter(id %in% ids) %>%
  mutate(first2=first.y1*-1)


```

## Getting Ropt for the selected individuals
```{r}

# Plotting to see if the conversion looks right
derivst%>%
  filter(id==165) %>%
  ggplot(aes(x=first.logtime, y=first2))+geom_line()

derivst%>%
  filter(id==301) %>%
  ggplot(aes(x=first.logtime, y=first2))+geom_line()

derivst%>%
  ggplot(aes(x=first.logtime, y=first2))+geom_line()+facet_wrap(~id)


# Getting the row with the maximum value for each individual
ropt<-derivst %>%
     group_by(id) %>%
     slice(which.max(first2))%>%
  mutate(logtime=first.logtime,
         ind=id)


```

## Getting the temperatures associated with the Ropt (Topt)
```{r}
oxall<-read.csv("./Outputs/oxygenall_aftercodedeletion.csv") #Use this one

#Merging the temperatures
topt<-difference_left_join(ropt,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup()


#getting the other demographic data
toptfinal_selected<-oxall %>%
  select(c("date", "trial", "channel", "ind", "stage", "weight", "ramp"))%>%
  filter(ind %in% ids) %>%
  group_by(ind)%>%
  filter(row_number()==1) %>%
  right_join(topt, by=c("ind"="ind.x")) %>%
  rename(logtime=logtime.x,
         tempcorr=tempcorr2,
         ropt1=first.y1, 
         ropt2=first2) %>%
  ungroup()%>%
  mutate(stage=fct_relevel(stage, levels=c("Protonymph", "Deutonymph", "Tritonymph", "Female", "Male" )))

levels(toptfinal_selected$stage)
#Visualizing the topt and Ropt

## Temperature optima
ggplot(toptfinal_selected, aes(x=stage, y=tempcorr))+geom_boxplot() +theme_classic() + 
  theme(text = element_text(size = 15))+
  xlab("Stage")+
  ylab("Ctmax (Celsius)")

ggplot(toptfinal, aes(x=stage, y=ropt2))+geom_boxplot() +theme_classic() + 
  theme(text = element_text(size = 15))+
  xlab("Stage")+
  ylab("Maximum rate of oxygen consumption")


write.csv(toptfinal, "Outputs/ToptandRopts.csv")
```



## Replacing old values for selected individuals
```{r}
dat<-read.csv("Outputs/ToptandRopts.csv")

topt2<-dat%>%
filter(!ind%in%ids) %>% #removing individuals that got redone
bind_rows(toptfinal_selected) %>% 
  filter_all(all_vars(!is.infinite(.)))
levels(as.factor(oxall$ind))


write.csv(topt2, "Outputs/ToptandRopts_manualtrimforsome.csv")
```





#############################################################################################

# Activation energy First try: one by one, ignore this one
```{r, eval=FALSE}
#Ind 2
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="2") %>% #filtering to each individual
  filter(between(first.logtime, 35, 65)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-2
energy<-data.frame(ind, slope,min,max)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 3
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="3") %>% #filtering to each individual
  filter(between(first.logtime, 35, 65)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-3
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 4
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="4") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-4
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 5
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="5") %>% #filtering to each individual
  filter(between(first.logtime, 40, 75)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-5
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 7
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="7") %>% #filtering to each individual
  filter(between(first.logtime, 50, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-7
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 10
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="10") %>% #filtering to each individual
  filter(between(first.logtime, 35, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-10
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 14
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="14") %>% #filtering to each individual
  filter(between(first.logtime, 35, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-14
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 18
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="18") %>% #filtering to each individual
  filter(between(first.logtime, 35, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-18
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 22
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="22") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-22
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 24
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="24") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-24
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 28
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="28") %>% #filtering to each individual
  filter(between(first.logtime, 40, 90)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-28
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 30
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="30") %>% #filtering to each individual
  filter(between(first.logtime, 40, 80)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-30
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

#Ind 29
## 1. Trim the first derivative from the closests left-sided minimum to the maximum value
indiv<-derivs%>%
  filter(id=="29") %>% #filtering to each individual
  filter(between(first.logtime, 40, 70)) # %>% #Triming the timeframe to the approximate relevant times (based on plot)
indiv %>%  ggplot(aes(x=first.logtime, y=first2))+geom_line() #Plotting to see what the line looks like
min<-indiv %>% slice(which.min(first2)) %>% select(first.logtime) #Getting the time where the minimum value is at
max<-indiv %>% slice(which.max(first2)) %>% select(first.logtime) #Getting the time where the maximum value is at
indiv<-indiv %>% filter(between(first.logtime, min, max))%>% #cutting the data to the max and minimum value
 mutate(logtime=first.logtime, ind=id) #changing variable names to facilitate merging later
indiv %>%  ggplot(aes(x=logtime, y=first2))+geom_line() #Plotting to see what the line looks like
## 2, 3, 4: Join data, kelvinf and log transformations
indiv<-difference_left_join(indiv,oxall, by=c("ind","logtime"), max_dist=0.13) %>% #Merges dataframes based on the closest logtime value (within 0.13)
  group_by(ind.x, logtime.x, first.y1, first2) %>%
  summarize(tempcorr2=mean(tempcorr)) %>% #averaging the tempcorr for when multiple cells are called
  ungroup() %>%
  mutate(tempk=tempcorr2+273.15, #converting temps to Kelvin
         lntempk=log(tempk), #converting kelvin to natural logarithm
         invlntempk=1/lntempk, #inverting the natural log of temp in K 
         lnderiv=log(first2)) #Getting the natural log of the derivative values
## 5: Getting the slope
model<-lm(lnderiv~invlntempk, data=indiv)
summary(model)
slope<-model$coefficients[2]
intercept<-model$coefficients[1]
## 6,7. Creating dataframe for the slope
ind<-29
dataframe<-data.frame(ind, slope)
energy<- bind_rows(energy, dataframe)
label<-paste("Individual ", ind, sep = "")
indiv %>%  ggplot(aes(x=invlntempk, y=lnderiv))+geom_point()+geom_abline(intercept = intercept, slope = slope, color="red", 
               linetype="solid", size=1.5) + ylim(-5,-3)+ theme_classic()+ theme(text = element_text(size = 15),plot.title = element_text(hjust=0.5))+ ggtitle(label)+
  xlab("1/lnTemp (K)")+
  ylab("ln(First derivative)")#Plotting to see what the line looks like
name<-paste("Individual_", ind, ".jpg", sep = "")
mypath <- file.path("Outputs/Activation energy plots/")
ggsave(plot=last_plot(),filename=name,  path=mypath)

```







Convert temperature to Kelvin
Cut all races t


plot1<-ggplot(data1,aes(x=logtime, y=oxymgl)+geom_point( pch=19)+ xlab('Logtime')+ ylab('Oxygen(mg/l)')+main(paste("Individual ", id)) +theme_classic()+theme(size=18)
lines(data$logtime, predict(fit, data.frame(logtime=data$logtime)), col='red',lwd=1.2)



revisaar si el numero imaginario no tiene un valor despreciable y no esta replicado, ahi si es de cuidado
