---
title: "Temperature analyses"
author: "Laura Segura Hernández"
date: "2022-08-06"
output:
  html_document:
    df_print: paged
    theme: cerulean
    toc: true
    toc_depth: 4
    number_sections: true
    toc_float: false
---

```{r setup, include=FALSE} 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
knitr::opts_knit$set(root.dir = "C:/Users/laus1/OneDrive - University of Nebraska-Lincoln/UNL/PhD Tesis/Methods/Thermolimit/Thermolimit data analyses")
getwd()
```


# Libraries
```{r}
library(data.table)
library(tidyr)
library(dplyr)
library(lubridate)
library(ggplot2)


```

# Organizing data

## Reading files

```{r}
cnames<-c("#", "datetime", "temp1", "temp2", "detached", "attached", "connected", "end","x")

t1.3<-read.csv("Data/Temperature/Thermal_block_trials1-3_1.csv", skip=2, header=F, col.names=cnames)

t4.7<-read.csv("Data/Temperature/Thermal_block_trials_4-7_0.csv", skip=2, header=F, col.names=cnames)

t8.13<-read.csv("Data/Temperature/Thermal_block_trials_8-13.csv", skip=2, header=F,col.names=cnames)

head(t1.3)

```

## Organizing and adding data


```{r}
t1.3<- t1.3 %>%
  na.omit() %>% #removing NAs
  select(1:4) %>% #removing non-relevant columns
  mutate(datetime=as_datetime(datetime, format="%m/%d/%y %I:%M:%S %p")) %>% #converting the datetime column from character into a datetime format 
  separate(datetime, c("date", "time"), remove=FALSE, sep=" ") %>% #separating date and time into two columns
  mutate(date=ymd(date), #formatting date 
         tempav=rowMeans(.[,5:6]), #calculating averages for the two temperature sensors
        trial=case_when(datetime >= ymd_hms("2022-06-21 09:53:00") &  
                               datetime <= ymd_hms("2022-06-21 10:50:00")~1, #Assigning trial 1
                        datetime >= ymd_hms("2022-06-21 14:58:00") &  
                               datetime <= ymd_hms("2022-06-21 17:08:00")~2,#Assigning trial 2
                        datetime >= ymd_hms("2022-06-21 18:19:00") &  
                               datetime <= ymd_hms("2022-06-21 20:28:00")~3,#Assigning trial 3
                        
                        TRUE~0))

t4.7<- t4.7 %>%
  na.omit() %>% #removing NAs
  select(1:4) %>% #removing non-relevant columns
  mutate(datetime=as_datetime(datetime, format="%m/%d/%y %I:%M:%S %p")) %>% #converting the datetime column from character into a datetime format 
  separate(datetime, c("date", "time"), remove=FALSE, sep=" ") %>% #separating date and time into two columns
  mutate(date=ymd(date), #formatting date 
         tempav=rowMeans(.[,5:6]), #calculating averages for the two temperature sensors
        trial=case_when(datetime >= ymd_hms("2022-06-22 11:07:00") &  
                               datetime <= ymd_hms("2022-06-22 13:19:00")~4, #Assigning trial 4
                        datetime >= ymd_hms("2022-06-22 14:10:00") &  
                               datetime <= ymd_hms("2022-06-22 16:24:00")~5,#Assigning trial 5
                        datetime >= ymd_hms("2022-06-22 17:26:00") &  
                               datetime <= ymd_hms("2022-06-22 19:50:00")~6,#Assigning trial 6
                        datetime >= ymd_hms("2022-06-22 20:23:00") &  
                               datetime <= ymd_hms("2022-06-22 22:29:00")~7,#Assigning trial 7
                        TRUE~0))


t8.13<- t8.13 %>%
  na.omit() %>% #removing NAs
  select(1:4) %>% #removing non-relevant columns 
  mutate(datetime=as_datetime(datetime, format="%m/%d/%y %I:%M:%S %p")) %>% #converting the datetime column from character into a datetime format 
  separate(datetime, c("date", "time"), remove=FALSE, sep=" ") %>% #separating date and time into two columns
  mutate(date=ymd(date), #formatting date 
          tempav=rowMeans(.[,5:6]), #calculating averages for the two temperature sensors
        trial=case_when(datetime >= ymd_hms("2022-06-23 09:37:00") &  
                               datetime <= ymd_hms("2022-06-23 11:48:00")~8, #Assigning trial 8
                        datetime >= ymd_hms("2022-06-23 12:39:00") &  
                               datetime <= ymd_hms("2022-06-23 14:56:00")~9,#Assigning trial 9
                        datetime >= ymd_hms("2022-06-23 15:38:00") &  
                               datetime <= ymd_hms("2022-06-23 17:55:00")~10,#Assigning trial 10
                        datetime >= ymd_hms("2022-06-23 18:33:00") &  
                               datetime <= ymd_hms("2022-06-23 20:50:00")~11,#Assigning trial 11
                        datetime >= ymd_hms("2022-06-23 21:43:00") &  
                               datetime <= ymd_hms("2022-06-24 00:00:00")~12,#Assigning trial 12
                        datetime >= ymd_hms("2022-06-24 00:44:00") &  
                               datetime <= ymd_hms("2022-06-24 03:01:00")~13,#Assigning trial 13
                        TRUE~0))

head(t1.3)
 

```

## Merging dataframes into a single one
```{r}
loggers<-bind_rows(t1.3,t4.7, t8.13) %>%
  mutate(datetime2=round_date(datetime, unit="minute")) #creating a coluns of datetime rounded by minutes to facilitate merging later

head(loggers)
```


## Creating dataframe for thermocouple variables
```{r}

# Trial 4
trial<-rep(4)
datetime<-c("2022-06-22 11:12:00", "2022-06-22 11:16:00","2022-06-22 11:48:00","2022-06-22 12:30:00","2022-06-22 12:55:00","2022-06-22 13:19:00")
tempblock<-c(30,30,38,48,55,57)
tempcouple<-c(28.3,28.3,37.1,47.1,53.7,55.5)

t4<-data.frame(trial, datetime,tempblock, tempcouple)
t4<-t4%>%
  mutate(datetime2=ymd_hms(datetime))


# Trial 5
trial<-rep(5)
datetime<-c("2022-06-22 14:14:00", "2022-06-22 14:34:00","2022-06-22 15:11:00","2022-06-22 15:45:00","2022-06-22 16:07:00","2022-06-22 16:18:00")
tempblock<-c(30,33,42,51,57,57)
tempcouple<-c(28.2,32.1,40.9,49.5,55.6,55.3)

t5<-data.frame(trial, datetime, tempblock,tempcouple)
t5<-t5%>%
  mutate(datetime2=ymd_hms(datetime))

# Trial 6
trial<-rep(6)
datetime<-c("2022-06-22 17:34:00", "2022-06-22 17:57:00","2022-06-22 18:27:00","2022-06-22 18:47:00","2022-06-22 19:07:00","2022-06-22 19:29:00", "2022-06-22 19:31:00", "2022-06-22 19:50:00")
tempblock<-c(30,33,40,45,50,56,56,57)
tempcouple<-c(28.1,32.2,38.9,43.7,48.6,54.7,54.7,55.5)

t6<-data.frame(trial, datetime,tempblock, tempcouple)
t6<-t6%>%
  mutate(datetime2=ymd_hms(datetime))

# Trial 7
trial<-rep(7)
datetime<-c("2022-06-22 20:25:00", "2022-06-22 21:37:00","2022-06-22 22:08:00","2022-06-22 22:18:00","2022-06-22 22:28:00")
tempblock<-c(30,46,54,56,57)
tempcouple<-c(27.2,44.9,52.8,54.7,55.6)

t7<-data.frame(trial, datetime,tempblock, tempcouple)
t7<-t7%>%
  mutate(datetime2=ymd_hms(datetime))

# Trial 8
trial<-rep(8)
datetime<-c("2022-06-23 09:39:00", "2022-06-23 09:45:00","2022-06-23 09:55:00","2022-06-23 10:08:00","2022-06-23 10:15:00","2022-06-23 10:25:00","2022-06-23 10:36:00","2022-06-23 10:46:00","2022-06-23 11:06:00","2022-06-23 11:16:00","2022-06-23 11:26:00","2022-06-23 11:30:00")
tempblock<-c(30,30,32,35,37,40,43,45,50,53,55,56)
tempcouple<-c(27.6,28.1,31.3,34.2,36.3,39.3,42.3,44.2,49.0,52.0,53.8,55)

t8<-data.frame(trial, datetime,tempblock, tempcouple)
t8<-t8%>%
  mutate(datetime2=ymd_hms(datetime))

# Trial 9
trial<-rep(9)
datetime<-c("2022-06-23 12:50:00", "2022-06-23 13:10:00","2022-06-23 14:01:00","2022-06-23 14:37:00")
tempblock<-c(30,34,47,56)
tempcouple<-c(29.0,33.2,46.2,55)

t9<-data.frame(trial, datetime,tempblock, tempcouple)
t9<-t9%>%
  mutate(datetime2=ymd_hms(datetime))

# Trial 10
trial<-rep(10)
datetime<-c("2022-06-23 15:48:00", "2022-06-23 16:08:00","2022-06-23 17:08:00","2022-06-23 17:33:00","2022-06-23 17:36:00","2022-06-23 17:56:00")
tempblock<-c(30,34,49,56,56,57)
tempcouple<-c(29.2,33.5,48.2,55.0,55,55)

t10<-data.frame(trial, datetime,tempblock, tempcouple)
t10<-t10%>%
  mutate(datetime2=ymd_hms(datetime))

# Trial 11
trial<-rep(11)
datetime<-c("2022-06-23 18:37:00", "2022-06-23 18:43:00","2022-06-23 20:00:00","2022-06-23 20:31:00","2022-06-23 20:42:00")
tempblock<-c(30,30,49,56,57)
tempcouple<-c(29,29.3,48.2,55.1,56)

t11<-data.frame(trial, datetime,tempblock, tempcouple)
t11<-t11%>%
  mutate(datetime2=ymd_hms(datetime))

# Trial 12
trial<-rep(12)
datetime<-c("2022-06-23 21:53:00", "2022-06-23 23:40:00","2022-06-23 23:41:00")
tempblock<-c(30,56,56)
tempcouple<-c(28.6,54.8,54.9)

t12<-data.frame(trial, datetime,tempblock, tempcouple)
t12<-t12%>%
  mutate(datetime2=ymd_hms(datetime))

# Trial 13
trial<-rep(13)
datetime<-c("2022-06-24 00:52:00", "2022-06-24 00:55:00","2022-06-24 01:51:00","2022-06-24 02:25:00","2022-06-24 02:42:00","2022-06-24 02:57:00")
tempblock<-c(30,30,43,52,56,57)
tempcouple<-c(28.5,28.9,42.4,50.8,54.9,56.1)

t13<-data.frame(trial, datetime,tempblock, tempcouple)
t13<-t13%>%
  mutate(datetime2=ymd_hms(datetime))


#Merging all into a single frame
couples<-bind_rows(t4,t5,t6,t7,t8,t9,t10,t11,t12,t13)

head(couples)

```


## Merging loggers and thermocouple data into a single dataframe
```{r}
all<-full_join(loggers, couples, by=c("datetime2","trial"), suffix=c("", ".cb"))
head(all)
```

# Exploring data

## Looking at the differences between loggers, thermalblock and thermocouple
```{r,fig.show="hold", out.width="50%"}
diffs<-all %>%
  mutate(diffblock=tempblock-tempav,
         diffcouple=tempcouple-tempav) %>%
  na.omit() 

head(diffs)

ggplot(diffs, aes(x=tempav,y=diffblock, color=trial))+
  geom_point()+ylim(-0.5,5) +theme_classic()+ggtitle("Difference between thermal block and loggers across temperatures")

ggplot(diffs, aes(x=tempav,y=diffcouple, color=trial))+
  geom_point()+ylim(-2.5,2.55)+theme_classic()+ggtitle("Difference between thermocouple  and loggers across temperatures")

ggplot(diffs, aes(x=tempav,y=tempblock, color=trial))+
  geom_point()+theme_classic()+ggtitle("Relationship between thermal block and loggers")

ggplot(diffs, aes(x=tempav,y=tempcouple, color=trial))+
  geom_point()+theme_classic()+ggtitle("Relationship between thermocouple and loggers")
```

***

> I think using the block temperatures would be better to correct the logger temperatures because:
 
1. The block sensor is always in the same position, but the thermocouple wire might have been placed on different spots or moved in between trials

2. The thermal block was done to keep track of specific temperatures to do PCRs, etc, therefore, it should be fairly accurate on how much the samples were heat up

***

#Correcting data

## Estimating the slope to correct the logger temperatures
```{r}
#Removing the extreme values
all2<-all%>%
  filter(X.!=1200) %>%
  filter(X.!=1201)


ggplot(all2, aes(x=tempav,y=tempblock, color=trial))+
  geom_point()+theme_classic()+ggtitle("Relationship between thermal block and loggers without outliers")

lm1<-lm(tempblock~tempav, data=all2)
lm1
slope<-lm1$coefficients[2]
int<-lm1$coefficients[1]
```

***

> As it is a linear relationship, I can now correct the loggers temps (x) to get the block temperature by using the formula:

\begin{align*}
y=m&x+b \\
o&r \\ 
block temperature = slope * l&ogger temperature + intercept \\
\end{align*}

***

## Correcting the temperatures for each trial
```{r}
# Removing trial 0 and correcting all other temperatures
all_corr<-all%>%
  filter(trial!=0) %>%
  mutate(tempcorr=(slope*tempav)+int)

head(all_corr)
```

## Estimating temperature slope for each trial

### Without removing bump at the begining of ramp
```{r, uncorrected}
# Trial 1
r1<-all_corr %>%
  filter(trial==1,
         datetime2 >= ymd_hms("2022-06-21 10:03:00") &  
                               datetime <= ymd_hms("2022-06-21 10:50:00"))  

ggplot(r1, aes(x=X.,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 1")

lmtemp<-lm(tempcorr~X., data=r1)
sl1<-lmtemp$coefficients[2]
round(sl1, digits=2)

# Trial 2
r2<-all_corr %>%
  filter(trial==2,
         datetime2 >= ymd_hms("2022-06-21 15:02:00") &  
                               datetime <= ymd_hms("2022-06-21 16:52:00"))  

ggplot(r2, aes(x=X.,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 2")

lmtemp<-lm(tempcorr~X., data=r2)
sl2<-lmtemp$coefficients[2]
round(sl2, digits=2) #it remains the same independentaly of removing the curve at the begining of the ramp or not
sl2 

# Trial 3
r3<-all_corr %>%
  filter(trial==3,
         datetime2 >= ymd_hms("2022-06-21 18:49:00") & datetime <= ymd_hms("2022-06-21 20:11:00"))  

ggplot(r3, aes(x=X.,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 3")

lmtemp<-lm(tempcorr~X., data=r3)
sl3<-lmtemp$coefficients[2]
round(sl3, digits=2) 
sl3 

# Trial 4
r4<-all_corr %>%
  filter(trial==4,
         datetime2 >= ymd_hms("2022-06-22 11:18:00") &  
                               datetime <= ymd_hms("2022-06-22 13:02:00")) %>%
  mutate(timeseq=seq(from=0, to=104,by=0.5))

ggplot(r4, aes(x=timeseq,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 4")

lmtemp<-lm(tempcorr~timeseq, data=r4)
sl4<-lmtemp$coefficients[2]
round(sl4, digits=2) 
sl4 

# Trial 5
r5<-all_corr %>%
  filter(trial==5,
         datetime2 >= ymd_hms("2022-06-22 14:23:00") &  
                               datetime <= ymd_hms("2022-06-22 16:06:00"))  %>%
  mutate(timeseq=seq(from=0, to=103,by=0.5))

ggplot(r5, aes(x=timeseq,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 5")

lmtemp<-lm(tempcorr~timeseq, data=r5)
sl5<-lmtemp$coefficients[2]
round(sl5, digits=2) 
sl5 

#Trial 6
r6<-all_corr %>%
  filter(trial==6,
         datetime2 >= ymd_hms("2022-06-22 17:38:00") &  
                               datetime <= ymd_hms("2022-06-22 19:32:00")) %>%
  mutate(timeseq=seq(from=0, to=114,by=0.5)) 

ggplot(r6, aes(x=timeseq,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 6")

lmtemp<-lm(tempcorr~timeseq, data=r6)
sl6<-lmtemp$coefficients[2]
round(sl6, digits=2) 
sl6 

#Trial 7
r7<-all_corr %>%
  filter(trial==7,
         datetime2 >= ymd_hms("2022-06-22 20:35:00") &  
                               datetime <= ymd_hms("2022-06-22 22:19:00"))  %>%
  mutate(timeseq=seq(from=0, to=104,by=0.5))

ggplot(r7, aes(x=timeseq,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 7")

lmtemp<-lm(tempcorr~timeseq, data=r7)
sl7<-lmtemp$coefficients[2]
round(sl7, digits=2) 
sl7 

#Trial 8
r8<-all_corr %>%
  filter(trial==8,
         datetime2 >= ymd_hms("2022-06-23 09:48:00") &  
                               datetime <= ymd_hms("2022-06-23 11:31:00"))  %>%
  mutate(timeseq=seq(from=0, to=103,by=0.5))

ggplot(r8, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 8")

lmtemp<-lm(tempcorr~timeseq, data=r8)
sl8<-lmtemp$coefficients[2]
round(sl8, digits=2) 
sl8

#Trial 9
r9<-all_corr %>%
  filter(trial==9,
         datetime2 >= ymd_hms("2022-06-23 13:08:00") &  
                               datetime <= ymd_hms("2022-06-23 14:38:00"))  %>%
  mutate(timeseq=seq(from=0, to=90,by=0.5))

ggplot(r9, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 9")

lmtemp<-lm(tempcorr~timeseq, data=r9)
sl9<-lmtemp$coefficients[2]
round(sl9, digits=2) 
sl9

#Trial 10
r10<-all_corr %>%
  filter(trial==10,
         datetime2 >= ymd_hms("2022-06-23 15:50:00") &  
                               datetime <= ymd_hms("2022-06-23 17:37:00"))  %>%
  mutate(timeseq=seq(from=0, to=107,by=0.5))

ggplot(r10, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 10")

lmtemp<-lm(tempcorr~timeseq, data=r10)
sl10<-lmtemp$coefficients[2]
round(sl10, digits=2) 
sl10

#Trial 11
r11<-all_corr %>%
  filter(trial==11,
         datetime2 >= ymd_hms("2022-06-23 18:45:00") &  
                               datetime <= ymd_hms("2022-06-23 20:32:00"))  %>%
  mutate(timeseq=seq(from=0, to=107,by=0.5))

ggplot(r11, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 11")

lmtemp<-lm(tempcorr~timeseq, data=r11)
sl11<-lmtemp$coefficients[2]
round(sl11, digits=2) 
sl11

#Trial 12
r12<-all_corr %>%
  filter(trial==12,
         datetime2 >= ymd_hms("2022-06-23 21:57:00") &  
                               datetime <= ymd_hms("2022-06-23 23:41:00"))  %>%
  mutate(timeseq=seq(from=0, to=104,by=0.5))

ggplot(r12, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 12")

lmtemp<-lm(tempcorr~timeseq, data=r12)
sl12<-lmtemp$coefficients[2]
round(sl12, digits=2) 
sl12

#Trial 13
r13<-all_corr %>%
  filter(trial==13,
         datetime2 >= ymd_hms("2022-06-24 00:58:00") &  
                               datetime <= ymd_hms("2022-06-24 02:43:00"))  %>%
  mutate(timeseq=seq(from=0, to=105,by=0.5))

ggplot(r13, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 13")

lmtemp<-lm(tempcorr~timeseq, data=r13)
sl13<-lmtemp$coefficients[2]
round(sl13, digits=2) 
sl13

slopes<-as.data.frame(c(sl1, sl2, sl3, sl4, sl5,sl6,sl7,sl8,sl9,sl10,sl11,sl12,sl13))
colnames(slopes)<-"uncorr"
```
### Removing bump at the begining of ramp

```{r, eval=TRUE}
# Trial 1
r1<-all_corr %>%
  filter(trial==1,
         datetime2 >= ymd_hms("2022-06-21 10:07:00") &  
                               datetime <= ymd_hms("2022-06-21 10:50:00"))  

ggplot(r1, aes(x=X.,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 1")

lmtemp<-lm(tempcorr~X., data=r1)
sl1<-lmtemp$coefficients[2]
round(sl1, digits=2)

# Trial 2
r2<-all_corr %>%
  filter(trial==2,
         datetime2 >= ymd_hms("2022-06-21 15:16:00") &  
                               datetime <= ymd_hms("2022-06-21 16:52:00"))  

ggplot(r2, aes(x=X.,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 2")

lmtemp<-lm(tempcorr~X., data=r2)
sl2<-lmtemp$coefficients[2]
round(sl2, digits=2) #it remains the same independentaly of removing the curve at the begining of the ramp or not
sl2 

# Trial 3
r3<-all_corr %>%
  filter(trial==3,
         datetime2 >= ymd_hms("2022-06-21 18:49:00") &  
                               datetime <= ymd_hms("2022-06-21 20:11:00"))  

ggplot(r3, aes(x=X.,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 3")

lmtemp<-lm(tempcorr~X., data=r3)
sl3<-lmtemp$coefficients[2]
round(sl3, digits=2) 
sl3 

# Trial 4
r4<-all_corr %>%
  filter(trial==4,
         datetime2 >= ymd_hms("2022-06-22 11:22:00") &  
                               datetime <= ymd_hms("2022-06-22 13:02:00")) %>%
  mutate(timeseq=seq(from=0, to=100,by=0.5))

ggplot(r4, aes(x=timeseq,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 4")

lmtemp<-lm(tempcorr~timeseq, data=r4)
sl4<-lmtemp$coefficients[2]
round(sl4, digits=2) 
sl4 

# Trial 5
r5<-all_corr %>%
  filter(trial==5,
         datetime2 >= ymd_hms("2022-06-22 14:27:00") &  
                               datetime <= ymd_hms("2022-06-22 16:06:00"))  %>%
  mutate(timeseq=seq(from=0, to=99,by=0.5))

ggplot(r5, aes(x=timeseq,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 5")

lmtemp<-lm(tempcorr~timeseq, data=r5)
sl5<-lmtemp$coefficients[2]
round(sl5, digits=2) 
sl5 

#Trial 6
r6<-all_corr %>%
  filter(trial==6,
         datetime2 >= ymd_hms("2022-06-22 17:47:00") &  
                               datetime <= ymd_hms("2022-06-22 19:32:00")) %>%
  mutate(timeseq=seq(from=0, to=105,by=0.5)) 

ggplot(r6, aes(x=timeseq,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 6")

lmtemp<-lm(tempcorr~timeseq, data=r6)
sl6<-lmtemp$coefficients[2]
round(sl6, digits=2) 
sl6 

#Trial 7
r7<-all_corr %>%
  filter(trial==7,
         datetime2 >= ymd_hms("2022-06-22 20:40:00") &  
                               datetime <= ymd_hms("2022-06-22 22:19:00"))  %>%
  mutate(timeseq=seq(from=0, to=99,by=0.5))

ggplot(r7, aes(x=timeseq,y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 7")

lmtemp<-lm(tempcorr~timeseq, data=r7)
sl7<-lmtemp$coefficients[2]
round(sl7, digits=2) 
sl7 

#Trial 8
r8<-all_corr %>%
  filter(trial==8,
         datetime2 >= ymd_hms("2022-06-23 09:52:00") &  
                               datetime <= ymd_hms("2022-06-23 11:31:00"))  %>%
  mutate(timeseq=seq(from=0, to=99,by=0.5))

ggplot(r8, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 8")

lmtemp<-lm(tempcorr~timeseq, data=r8)
sl8<-lmtemp$coefficients[2]
round(sl8, digits=2) 
sl8

#Trial 9
r9<-all_corr %>%
  filter(trial==9,
         datetime2 >= ymd_hms("2022-06-23 13:08:00") &  
                               datetime <= ymd_hms("2022-06-23 14:38:00"))  %>%
  mutate(timeseq=seq(from=0, to=90,by=0.5))

ggplot(r9, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 9")

lmtemp<-lm(tempcorr~timeseq, data=r9)
sl9<-lmtemp$coefficients[2]
round(sl9, digits=2) 
sl9

#Trial 10
r10<-all_corr %>%
  filter(trial==10,
         datetime2 >= ymd_hms("2022-06-23 15:55:00") &  
                               datetime <= ymd_hms("2022-06-23 17:37:00"))  %>%
  mutate(timeseq=seq(from=0, to=102,by=0.5))

ggplot(r10, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 10")

lmtemp<-lm(tempcorr~timeseq, data=r10)
sl10<-lmtemp$coefficients[2]
round(sl10, digits=2) 
sl10

#Trial 11
r11<-all_corr %>%
  filter(trial==11,
         datetime2 >= ymd_hms("2022-06-23 19:02:00") &  
                               datetime <= ymd_hms("2022-06-23 20:32:00"))  %>%
  mutate(timeseq=seq(from=0, to=90,by=0.5))

ggplot(r11, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 11")

lmtemp<-lm(tempcorr~timeseq, data=r11)
sl11<-lmtemp$coefficients[2]
round(sl11, digits=2) 
sl11

#Trial 12
r12<-all_corr %>%
  filter(trial==12,
         datetime2 >= ymd_hms("2022-06-23 22:00:00") &  
                               datetime <= ymd_hms("2022-06-23 23:41:00"))  %>%
  mutate(timeseq=seq(from=0, to=101,by=0.5))

ggplot(r12, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 12")

lmtemp<-lm(tempcorr~timeseq, data=r12)
sl12<-lmtemp$coefficients[2]
round(sl12, digits=2) 
sl12

#Trial 13
r13<-all_corr %>%
  filter(trial==13,
         datetime2 >= ymd_hms("2022-06-24 01:01:00") &  
                               datetime <= ymd_hms("2022-06-24 02:43:00"))  %>%
  mutate(timeseq=seq(from=0, to=102,by=0.5))

ggplot(r13, aes(x=timeseq, y=tempcorr))+
  geom_point()+theme_classic()+ggtitle("Trial 13")

lmtemp<-lm(tempcorr~timeseq, data=r13)
sl13<-lmtemp$coefficients[2]
round(sl13, digits=2) 
sl13
```

### Comparing slopes
```{r, eval=TRUE}
slopes$corr<-c(sl1, sl2, sl3, sl4, sl5,sl6,sl7,sl8,sl9,sl10,sl11,sl12,sl13)
slopes2<-slopes %>%
  mutate(uncround=round(uncorr, digits=2),
         corround=round(corr, digits=2),
         comparison= (uncround-corround))
slopes2
mean(slopes2$uncround)
mean(slopes2$corround)

```

***

# ASK FOR SECOND OPINION!!!

It seems like either group of slopes (mean corrected = 0.2485 ~ 0.25 or not corrected- mean=0.2446 ~ 0.24) shows similar slopes. I will use the uncorrected ones for the analyses

***




## Adding ramping slope to the dataframe




```{r}
all_corr<-all_corr %>%
  mutate(ramp=case_when(trial==1~sl1,
                        trial==2~sl2,
                        trial==3~sl3,
                        trial==4~sl4,
                        trial==5~sl5,
                        trial==6~sl6,
                        trial==7~sl7,
                        trial==8~sl8,
                        trial==9~sl9,
                        trial==10~sl10,
                        trial==11~sl11,
                        trial==12~sl12,
                        trial==13~sl13,
                        TRUE~0))
```



```{r}
write.csv(all_corr, "Outputs/temperatures_corrected.csv")
```

## Plotting corrected vs raw temperatures
```{r, fig.show="hold", out.width="50%"}
p1<-all_corr %>%
  filter(trial==1) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 1")
p1

p2<-all_corr %>%
  filter(trial==2) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 2")
p2

p3<-all_corr %>%
  filter(trial==3) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 3")
p3

p4<-all_corr %>%
  filter(trial==4) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 4")
p4


p5<-all_corr %>%
  filter(trial==5) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 5")
p5

p6<-all_corr %>%
  filter(trial==6) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 6")
p6

p7<-all_corr %>%
  filter(trial==7) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 7")
p7

p8<-all_corr %>%
  filter(trial==8) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 8")
p8

p9<-all_corr %>%
  filter(trial==9) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 9")
p9

p10<-all_corr %>%
  filter(trial==10) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 10")
p10

p11<-all_corr %>%
  filter(trial==11) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 11")
p11

p12<-all_corr %>%
  filter(trial==12) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 12")
p12

p13<-all_corr %>%
  filter(trial==13) %>%
  pivot_longer(cols=c("tempav", "tempcorr"), values_to="temps", names_to = "type")%>%
  ggplot(.,aes(x=time,y=temps, color=type))+
  geom_point()+theme_classic()+ylim(25,57)+ ggtitle("Trial 13")
p13
```

# Saving workspace file

```{r, eval=FALSE}
#save(list = ls(.GlobalEnv), file = "Outputs/Temperature analyses.RData") #saves all the objects in the global environment
save(all_corr,file = "Outputs/Temperature analyses.RData")
```


